---
title: "3.5: Species parameterisation for `drum_croaker`"
subtitle: "FAO Climate Change Risks to Fed Mariculture"
author: 
  - "Tormey Reimer"
date: last-modified
---

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Parameterise species: `rainbow_trout`](03_04_check_species_rainbow_trout.qmd)

[Next: Parameterise species: `golden_pompano` →](03_05_check_species_golden_pompano.qmd)
:::

# Overview {#sec-overview}

```{r setup}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false

library(tidyverse)
library(here)
library(readxl)
library(janitor)
library(lhs)
library(scales)
library(gt)
library(qs2)
library(janitor)
library(slider)
```

```{r source-scripts}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: Source R scripts in use

here("src", "dirs.R") %>% source()
here("src", "model_functions.R") %>% source()
here("src", "display_globals.R") %>% source()
```

This document runs the checking and calibration process on the `drum_croaker` model. For a full description of the process, see [parameterise_species_seabream](03_01_check_species_seabream.qmd). 

# Species parameters {#sec-species-params}

As we are only running a single representative individual, the Monte-Carlo parameters are not in use.

```{r load-parameters}
#| code-summary: Load species parameters for drum_croaker

this_species <- "drum_croaker"

parameters_species <- read_excel(
  file.path(rawdata_path, 'parameters_species.xlsx'),
  sheet = this_species,
  trim_ws = T,
  n_max = 28
) %>%
  clean_names() %>% 
  select(used_in_script, value, flexibility)

species_params <- parameters_species %>% pull(value) %>% as.numeric()
names(species_params) <- parameters_species %>% pull(used_in_script)

species_params[["overFmean"]] <- 0.025
species_params[["overFdelta"]] <- 0.0025
```

# Environmental/feed parameters {#sec-environmental-params}

```{r feed-params}
#| code-summary: Load feed and ingredient data and calculate feed composition parameters

feeds_df <- read_excel(here("data", "raw_data", "feed_profiles_and_composition.xlsx"), sheet = "all_feeds") %>%
  select(feed, ingredient, proportion) %>% 
  filter(feed == "Large Yellow Croaker 1")

ingredients_df <- read_excel(here("data", "raw_data", "all_ingredients.xlsx"), sheet = "all_ingredients") %>% 
  select(ingredient, protein, lipid, carb)

digestibility_df <- read_excel(here("data", "raw_data", "all_ingredients.xlsx"), sheet = "all_ingredients") %>% 
  clean_names() %>% 
  rename(
    protein_digestibility = mean_protein_digestibility, 
    lipid_digestibility = mean_lipid_digestibility, 
    carb_digestibility = mean_carb_digestibility
  ) %>% 
  select(ingredient, protein_digestibility, lipid_digestibility, carb_digestibility)

feed_params <- sum_feeds(
  format_feeds(feeds_df, ingredients_df, digestibility_df)
  )[[1]]

qs_save(feed_params, file.path(prepdata_path, "feed_parameters", "feed_parameters_drum_croaker.qs"))
```

```{r tbl-feed-nutrition}
#| code-summary: Show feed nutritional profile
#| tbl-cap: "Nutritional profile of the feed for this species."

tibble(
  Macronutrient = c("Protein", "Lipid", "Carbohydrate"),
  Proportion = c(feed_params[["protein"]]$macro, feed_params[["lipid"]]$macro, feed_params[["carb"]]$macro),
  Digestibility = c(feed_params[["protein"]]$digestibility, feed_params[["lipid"]]$digestibility, feed_params[["carb"]]$digestibility)
) |>
  gt() |>
  fmt_percent(columns = c(Proportion, Digestibility), decimals = 1)
```

The temperature timeseries used is based on the mean current temperatures at farms assigned to this model group in [02_assigning_locations](02_assigning_locations.qmd).

```{r environmental-params}
#| code-summary: Define simulation times and temperature timeseries

# Get current mean temperatures for farms assigned to this model
farm_temps_all <- file.path(prepdata_path, "farm_temps_bymodel", "meanyear_farm_temps_drum_croaker.qs") %>% 
  qs_read() %>% 
  group_by(model_name, doy) %>% 
  reframe(sst = mean(sst))

farm_temps_all <- rbind(
  farm_temps_all,
  farm_temps_all %>% mutate(doy = doy + 365),
  farm_temps_all %>% mutate(doy = doy + 730)
)

# Get feeding response at each DOY
farm_temps_all$fr <- sapply(
    X = farm_temps_all$sst, 
    FUN = feeding_rate, 
    species_params = species_params
  )
farm_temps_all$fr[is.na(farm_temps_all$fr)] <- 0

# Get a good growing window
grow_days <- species_params[["gd"]] %>% as.integer()
gds <- farm_temps_all %>% 
  mutate(
    roll_fr = slide_dbl(fr, sum, .before = 0, .after = grow_days - 1)
  ) %>%
  slice(1:(nrow(farm_temps_all) - grow_days + 1)) %>%
  slice_max(roll_fr, n = 1) %>%
  mutate(end_doy = doy + grow_days - 1)

times <- c(
  t_start = gds$doy[1],
  t_end   = gds$end_doy[1],
  dt      = 1L
)

farm_temps <- farm_temps_all %>% 
  filter(doy >= times['t_start'] & doy <= times['t_end'])

# ggplot(farm_temps, aes(x = doy, y = sst)) +
#   geom_line() +
#   theme_classic()
```

# Run model with raw parameters {#sec-run-model-raw}

```{r check-inputs}
#| code-summary: Check that all parameters being passed to the model functions are correct

check_fish_growth_inputs(
  species_params = species_params,
  water_temp     = farm_temps$sst,
  feed_params    = feed_params,
  times          = c(
    "t_start" = min(farm_temps$doy),
    "t_end" = max(farm_temps$doy),
    "dt" = 1
  ),
  init_weight    = species_params['meanW'],
  ingmax         = species_params['meanImax']
)
```

```{r run-model}
#| code-summary: Run fish_growth() for a representative individual

set.seed(42)
one_fish <- fish_growth(
  species_params = species_params,
  water_temp     = farm_temps$sst,
  feed_params    = feed_params,
  times          = c(
    "t_start" = min(farm_temps$doy),
    "t_end" = max(farm_temps$doy),
    "dt" = 1
  ),
  init_weight    = species_params['meanW'],
  ingmax         = species_params['meanImax']
)

cat(sprintf(
  'Initial weight: %.1f g  |  Final weight: %.1f g (%.1f g)  |  Approx. FCR: %.2f |  Final SGR: %.1f \n',
  one_fish[1, 'weight'],
  tail(one_fish[, 'weight'], 1), species_params['CS'],
  sum(one_fish[, 'food_prov'], na.rm = T) / (tail(one_fish[, 'weight'], 1) - one_fish[1, 'weight']),
  tail(one_fish[, 'SGR'], 1)
))
```

The model outputs here are looking ok, but harvest size is being substantially overestimated (@fig-outputs). Many of the parameters for this species are placeholder values taken from the `atlantic_salmon` model, which has a much larger harvest size.

```{r fig-outputs}
#| code-summary: Plot all fish_growth() outputs facetted by measure
#| fig-cap: "All fish_growth() output variables for a representative individual over a single grow-out period using the default temperature timeseries and feed composition."
#| fig-height: 10
#| echo: false
#| warning: false
#| message: false

of_df <- as.data.frame(one_fish) %>%
  pivot_longer(
    cols      = !contains('days'),
    names_to  = 'output_var',
    values_to = 'value'
  )

plot_sim_results(of_df, CS = species_params["CS"])
```

# Model sensitivity {#sec-sensitivity}

```{r set-parameter-flexibility}
#| code-summary: Set uncertainty of parameters (and remove parameters not being tested for sensitivity)

# "flexibility" refers to the flexibility I'm willing to give each parameter (ie uncertainty)
flex_params <- parameters_species %>% 
  select(param = used_in_script, flexibility) %>% 
  filter(!is.na(flexibility)) %>% 
  arrange(flexibility)
```

```{r parameter-sensitivity}
#| code-summary: Calculate parameter sensitivity for weight and SGR across plus-minus 10 percent parameter perturbations

species_params_sens <- map(
  flex_params$param,
  function(nm) {
    map(c(0.9, 1.0, 1.1), function(level) {
      species_params[nm] <- species_params[nm] * level
      species_params
    }) %>% 
      setNames(c("low", "med", "high"))
  }
) %>% 
  setNames(flex_params$param)

set.seed(42)
sens_results <- map2_dfr(
  species_params_sens, 
  names(species_params_sens),
  function(sp, nm) {
    map_dfr(sp, function(sp_lev) {
      fish_growth(
        species_params = sp_lev,
        water_temp     = farm_temps$sst,
        feed_params    = feed_params,
        times          = c(
          "t_start" = min(farm_temps$doy),
          "t_end" = max(farm_temps$doy),
          "dt" = 1
        ),
        init_weight    = sp_lev['meanW'],
        ingmax         = sp_lev['meanImax']
      ) %>% 
        as.data.frame() %>% 
        tail(1) %>% 
        select(weight, SGR)
    }) %>% 
      mutate(
        param = nm, 
        level = names(sp)
      )
  }
) 

# Calculate sensitivity
sens_results <- sens_results %>%
  group_by(param) %>%
  summarise(across(c(weight, SGR), ~ (.x[level == "high"] - .x[level == "low"]) / (.x[level == "med"] * 0.2), .names = "{.col}")) %>% 
  pivot_longer(
    cols = !contains("param"),
    values_to = "sens", names_to = "output",
    names_transform = c(output = as.factor)
  ) %>% 
  left_join(flex_params, by = "param") %>% 
  mutate(param = factor(param, levels = rev(flex_params$param)))
```

@fig-sensitivity shows how sensitive the model output (individual weight/SGR) is to changes in each parameter - ie the positive/negative impact of increasing that parameter by 10%.

```{r fig-sensitivity}
#| code-summary: Plot parameter sensitivity as a barplot facetted by output variable
#| fig-cap: "Sensitivity of final weight and SGR to ±10% perturbations of each model parameter. Values represent the proportional change in output per unit change in parameter."
sens_results %>%
  ggplot(aes(x = param, y = sens, fill = output)) +
  geom_col(colour = "black") +
  coord_flip() +
  facet_wrap(~output) +
  prettyplot()
```

# Hypercube adjustment {#sec-hypercube}

The hypercube adjustment uses Latin Hypercube Sampling (LHS) to search for parameter combinations that bring model output closer to the target weight (commercial size). 

```{r hypercube-ranges}
#| code-summary: Calculate per-parameter sampling ranges from sensitivity and flexibility

# Combine sensitivity across both output variables (mean absolute sensitivity)
sens_combined <- sens_results %>%
  group_by(param, flexibility) %>%
  summarise(mean_abs_sens = mean(abs(sens)), .groups = "drop")

# Range score: inversely proportional to mean absolute sensitivity and flexibility rank.
# Cap 1/sens to avoid blow-up when sensitivity is near zero.
max_inv_sens <- 20
min_inv_sens <- 0.1
sens_combined <- sens_combined %>%
  mutate(
    inv_sens  = pmax(min_inv_sens, pmin(1 / pmax(mean_abs_sens, 1 / max_inv_sens), max_inv_sens)),
    raw_range = inv_sens * (1 / flexibility)
  )

# Cap range changes at +-10%
sens_combined <- sens_combined %>%
  mutate(
    param        = as.character(param),
    sample_range = scales::rescale(raw_range, to = c(0.005, 0.10))
  )
```

```{r fig-hypercube-ranges}
#| code-summary: Plot sampling ranges per parameter
#| fig-cap: "LHS sampling range (as a proportion of baseline value) for each parameter. Wider bars indicate parameters that are less sensitive and/or more flexible, giving the sampler more room to explore. Sampling range is capped at +-10% of baseline."
#| fig-height: 5
#| fig-width: 7

sens_combined %>%
  mutate(param = factor(param, levels = param[order(sample_range)])) %>%
  ggplot(aes(x = param, y = sample_range * 100)) +
  geom_col(fill = "#2171b5", colour = "black", width = 0.7) +
  coord_flip() +
  labs(x = "Parameter", y = "Sampling range (+-% of baseline)") +
  theme_classic()
```

```{r hypercube-targets}
#| code-summary: Define target experimental data as a list of experiments - each with its own temperature timeseries and named target outputs

# Each entry in `target_experiments` represents one experimental condition.
# `water_temp` : data.frame with columns `day` (integer) and `temp_C` (numeric)
#                matching that experiment's temperature conditions.
# `targets`    : a named numeric vector of any model output columns to fit.
#                Different experiments can supply different (or overlapping) outputs.

# SS fitness is computed as the MEAN squared error across all (experiment × output)
# observations, so experiments with more targets do not dominate the fit.
target_experiments <- list(
  list(
    water_temp = farm_temps$sst,
    targets    = c(weight_change = unname(species_params["CS"] - species_params["meanW"])),
    meanW      = species_params["meanW"]
  )
)

n_pairs <- length(target_experiments)

# This function processes the fish_growth() output to get it ready for comparison. It's defined here so that if different comparisons are added in this chunk I can change the calculation everywhere at once
get_comparison_stats <- function(df) {
  dfdf <- as.data.frame(df)
  data.frame(
    weight_change = tail(dfdf$weight, 1) - head(dfdf$weight, 1),
    SGR = tail(dfdf$SGR, 1)
  )
}
```

```{r hypercube-sample}
#| code-summary: Generate LHS parameter samples and run model for each (1000 samples x n_pairs with progress updates every 100)

n_samples     <- 2500
param_names   <- sens_combined$param
sample_ranges <- sens_combined$sample_range
n_params      <- length(param_names)

set.seed(42)
lhs_raw <- randomLHS(n_samples, n_params)

# Map [0, 1] to [1 - range, 1 + range] multipliers for each parameter
multiplier_matrix <- sweep(lhs_raw * 2 - 1, 2, sample_ranges, "*") + 1
colnames(multiplier_matrix) <- param_names

# Run model once per experiment for each LHS sample.
# All final-row model output columns are retained so any named target can be used.
lhs_results <- vector("list", n_samples)
start_time  <- proc.time()["elapsed"]

for (i in seq_len(n_samples)) {
  if (i %% 500 == 0) {
    elapsed <- round(proc.time()["elapsed"] - start_time, 1)
    rate    <- i / elapsed
    eta     <- round((n_samples - i) / rate, 1)
    cat(sprintf(
      "Sample %4d / %d | elapsed: %.0fs | ETA: %.0fs\n",
      i, n_samples, elapsed, eta
    ))
  }

  sp <- species_params
  for (j in param_names) {
    sp[j] <- species_params[j] * multiplier_matrix[i, j]
  }

  # Run once per experiment; keep all output columns from the final timestep
  pair_results <- vector("list", n_pairs)
  for (k in seq_len(n_pairs)) {
    wt <- target_experiments[[k]]$water_temp

    change_params <- names(target_experiments[[k]])[names(target_experiments[[k]]) %in% names(species_params)]
    if (length(change_params) > 0) {
      for (c in change_params) {
        sp[c] <- unlist(target_experiments[[k]][c])
      }      
    }

    result <- tryCatch(
      fish_growth(
        species_params = sp,
        water_temp     = wt,
        feed_params    = feed_params,
        times          = c(
          "t_start" = 1,
          "t_end"   = length(wt),
          "dt"      = 1
        ),
        init_weight = sp["meanW"],
        ingmax      = sp["meanImax"]
      ),
      error = function(e) NULL
    )
    if (!is.null(result)) {
      final <- get_comparison_stats(result)
      pair_results[[k]] <- final %>% mutate(sample = i, pair = k, .before = 1)
    }
  }

  pair_df <- bind_rows(pair_results)
  # Only retain samples where all experiments completed successfully
  if (nrow(pair_df) == n_pairs) {
    lhs_results[[i]] <- pair_df
  }
}

cat(sprintf(
  "Done. Total time: %.1fs\n",
  proc.time()["elapsed"] - start_time
))

# One row per (sample, experiment)
lhs_results_df <- bind_rows(lhs_results)
```

```{r hypercube-fitness}
#| code-summary: Calculate absolute weight difference between modelled and target weight change for each LHS sample

target_wt_change <- target_experiments[[1]]$targets[["weight_change"]]

# Absolute difference between modelled and target weight change per sample
lhs_fit_df <- lhs_results_df %>%
  group_by(sample) %>%
  summarise(abs_diff = abs(weight_change - target_wt_change), .groups = "drop")

# Attach multipliers for inspection of top-performing samples
multipliers_df <- as.data.frame(multiplier_matrix) %>%
  mutate(sample = seq_len(n_samples))

lhs_fit_df <- lhs_fit_df %>%
  left_join(multipliers_df, by = "sample")

# Baseline: run the unadjusted model and compute absolute difference
baseline_result <- fish_growth(
  species_params = species_params,
  water_temp     = target_experiments[[1]]$water_temp,
  feed_params    = feed_params,
  times          = c(
    "t_start" = 1,
    "t_end"   = length(target_experiments[[1]]$water_temp),
    "dt"      = 1
  ),
  init_weight = species_params["meanW"],
  ingmax      = species_params["meanImax"]
)

baseline_abs_diff <- abs(get_comparison_stats(baseline_result)$weight_change - target_wt_change)

cat(sprintf(
  "Samples completed: %d / %d\n",
  n_distinct(lhs_fit_df$sample), n_samples
))
```

@fig-hypercube-abs-diff shows the distribution of absolute weight differences across all samples.

```{r fig-hypercube-abs-diff}
#| code-summary: Plot distribution of absolute weight differences across all LHS samples
#| fig-cap: "Distribution of absolute differences between modelled and target weight change across all LHS samples. Lower values indicate better fit to the target data. The red dashed line shows the baseline (unadjusted) absolute difference."
#| fig-height: 4
#| fig-width: 7

lhs_fit_df %>%
  ggplot(aes(x = abs_diff)) +
  geom_histogram(bins = 50, fill = "#2171b5", colour = "black", linewidth = 0.2) +
  geom_vline(xintercept = baseline_abs_diff, colour = "red", linetype = "dashed") +
  labs(x = "Absolute weight difference (g)", y = "Count") +
  theme_classic()
```

The parameter multipliers for the best-fitting sample (relative to baseline) are:

```{r tbl-hypercube-best-params}
#| code-summary: Show parameter multipliers for the best-fitting sample
#| tbl-cap: "Parameter multipliers and adjusted values for the best-fitting LHS sample. Parameters are sorted by the magnitude of their percentage change from baseline."

best_sample <- lhs_fit_df %>%
  arrange(abs_diff) %>%
  slice_head(n = 1) %>%
  pull(sample)

best_lhs_results <- lhs_fit_df %>%
  filter(sample == best_sample) %>%
  select(all_of(param_names)) %>%
  pivot_longer(everything(), names_to = "param", values_to = "multiplier") 
  
# If the change is extremely small (<0.05% of baseline) then the baseline version is kept
best_lhs_results <- best_lhs_results %>%
  mutate(
    multiplier    = case_when(round(multiplier, 2) == 1.00 ~ 1, T ~ multiplier),
    pct_change    = (multiplier - 1) * 100,
    baseline_val  = species_params[param],
    adjusted_val  = baseline_val * multiplier
  ) %>%
  filter(multiplier != 1) %>% 
  arrange(desc(abs(pct_change)))

best_lhs_results %>%
  gt() %>%
  fmt_number(columns = c(multiplier, pct_change), decimals = 2) %>%
  fmt_number(columns = c(baseline_val, adjusted_val), decimals = 4) %>% 
  cols_label(
    param        = "Parameter",
    multiplier   = "Multiplier",
    pct_change   = "% change",
    baseline_val = "Raw value",
    adjusted_val = "Calibrated value"
  )
```

# Calibrated run {#sec-calibrated}

```{r display-new-values}
#| code-summary: Replace calibrated species parameters with new values

new_params <- best_lhs_results$adjusted_val
names(new_params) <- best_lhs_results$param
species_params_new <- species_params
for(nm in names(new_params)) {
  species_params_new[nm] <- new_params[nm]
}
species_params_new["gd"] <- round(species_params_new["gd"], 0)

spn <- data.frame(
  Parameter = names(species_params_new),
  Original_Value = unname(species_params),
  New_Value = unname(species_params_new),
  Pct_Change = 100*unname((species_params-species_params_new)/species_params)
)
```

```{r run-calibrated-model}
#| code-summary: Run fish_growth() with the calibrated parameter values

# Run with the default temperature timeseries for the trajectory plot (same as
# the initial checks above), giving a single representative growth trajectory.
set.seed(42)

times <- c(
  "t_start" = gds$doy[1],
  "t_end"   = gds$doy[1] + unname(species_params_new["gd"]) - 1,
  "dt"      = 1
)

farm_temps_new <- farm_temps_all %>% 
  filter(doy >= times['t_start'] & doy <= times['t_end'])

one_fish_new <- fish_growth(
  species_params = species_params_new,
  water_temp     = farm_temps_new$sst,
  feed_params    = feed_params,
  times          = times,
  init_weight    = species_params_new['meanW'],
  ingmax         = species_params_new['meanImax']
)

# Also validate against each paired experimental temperature series to confirm
# that the best parameter set improves fit across all observed conditions.
calibrated_pair_results <- map_dfr(seq_len(n_pairs), function(k) {
  wt <- target_experiments[[k]]$water_temp
  sp <- species_params_new
  if (!is.null(target_experiments[[k]]$initW)) {sp["meanW"] <- target_experiments[[k]]$initW}
  set.seed(42)
  result <- fish_growth(
    species_params = sp,
    water_temp     = wt,
    feed_params    = feed_params,
    times          = c(
      "t_start" = 1,
      "t_end"   = length(wt),
      "dt"      = 1
    ),
    init_weight = sp['meanW'],
    ingmax      = sp['meanImax']
  )
  get_comparison_stats(result) %>% mutate(pair = k)
})

# Summary comparison: calibrated vs. target per experiment
# Only columns that appear in each experiment's `targets` vector are shown.
calibrated_summary <- map_dfr(seq_len(n_pairs), function(k) {
  row  <- calibrated_pair_results %>% filter(pair == k)
  tgts <- target_experiments[[k]]$targets
  map_dfr(names(tgts), function(col) {
    data.frame(
      pair      = k,
      output    = col,
      modelled  = row[[col]],
      target    = tgts[[col]],
      diff      = row[[col]] - tgts[[col]]
    )
  })
})

```

```{r tbl-calibrated-summary}
#| code-summary: Display modelled vs target values for each experiment after calibration
#| tbl-cap: "Comparison of calibrated model output against target values for each experiment."

calibrated_summary %>%
  gt() %>%
  fmt_number(columns = c(modelled, target, diff), decimals = 2) %>% 
  cols_label(
    pair     = "Run",
    output   = "Output variable",
    modelled = "Modelled",
    target   = "Target",
    diff     = "Difference"
  )
```

@fig-outputs-calibrated shows all output variables over the grow-out period.

```{r fig-outputs-calibrated}
#| code-summary: Plot all calibrated fish_growth() outputs facetted by measure
#| fig-cap: "All fish_growth() output variables for a representative individual over a single grow-out period using the default temperature timeseries and feed composition, with the the calibrated parameter values."
#| fig-height: 10
#| echo: false
#| warning: false
#| message: false

ofn <- as.data.frame(one_fish_new) %>%
  pivot_longer(
    cols      = !contains('days'),
    names_to  = 'output_var',
    values_to = 'value'
  )

plot_sim_results(ofn, CS = species_params_new["CS"])
```

```{r save-params}
#| code-summary: Save calibrated species parameters

qd_save(
  species_params_new, 
  file.path(prepdata_path, "species_parameters", "species_parameters_drum_croaker.qs")
)
```

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Parameterise species: `rainbow_trout`](03_04_check_species_rainbow_trout.qmd)

[Next: Parameterise species: `golden_pompano` →](03_05_check_species_golden_pompano.qmd)
:::
