---
title: "3.2: Species temperature responses"
subtitle: "FAO Climate Change Risks to Fed Mariculture"
author:
  - "Tormey Reimer"
date: last-modified
---

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Choosing species](01_choosing_species.qmd)

[Next: Assigning Locations →](04_assigning_locations.qmd)
:::

# Overview {#sec-overview}

```{r setup}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: "Load packages and set display globals"

library(tidyverse)
library(patchwork)
library(terra)
library(qs2)
library(terra)
library(tidyterra)
library(sf)
library(rnaturalearth)
library(lubridate)
library(cmocean)
library(here)
```

```{r source-scripts}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: "Source R scripts in use"

here("src", "dirs.R") %>% source()
here("src", "functions.R") %>% source()
here("src", "model_functions.R") %>% source()
here("src", "display_globals.R") %>% source()
```

The species temperature response is critical within this model and study, as it determines two fundamental responses:

* The feeding response of the individual
* The metabolic response of the individual

The feeding response also informs the individual's preferred temperature range, which informs the farms that are assigned to that species.

# Species parameters {#sec-species-params}

```{r load-parameters}
#| code-summary: 'Load species parameters for all models'

params_files <- file.path(prepdata_path, "species_parameters") %>% 
  list.files(full.names = T)

model_names <- params_files %>% 
  basename() %>% 
  str_remove_all("species_parameters_|.qs")

parameters_species <- map(params_files, qd_read) %>% 
  setNames(model_names)

parameters_feeds <- map(list.files(file.path(prepdata_path, "feed_parameters"), full.names = T), qs_read) %>% 
  setNames(model_names)
```

```{r metabolic-response-functions}
#| code-summary: A single function to get all the species-specific temperature responses

get_species_responses <- function(water_temp, species_params, feed_params, ref_weight) {
  fr             <- sapply(water_temp, feeding_rate, species_params = species_params)
  T_response     <- exp(species_params['pk'] * water_temp)
  feed_ingested  <- species_params['meanImax'] * (ref_weight^species_params['m']) * fr

  E_assim <- map_dfr(
    feed_ingested, 
    function(fi) {
      map_dfr(names(feed_params), function(nm) {
        apportion_feed(fi, fi, feed_params[[nm]]$proportion, feed_params[[nm]]$macro, feed_params[[nm]]$digestibility)['assimilated']
        }) %>% 
        mutate(macro = names(feed_params)) %>% 
        pivot_wider(names_from = macro, values_from = assimilated)
    }) %>% 
      mutate(
        protein = protein * species_params['epsprot'],
        lipid = lipid * species_params['epslip'],
        carb = carb * species_params['epscarb'],
        total = protein + lipid + carb
      )
  
  anab      <- E_assim$total * (1 - species_params['alpha'])
  catab     <- species_params['epsO2'] * species_params['k0'] * T_response * (ref_weight^species_params['n']) * species_params['omega'] # catabolic response
  E_somat   <- rep(species_params['a'] * ref_weight^species_params['k'], length(water_temp))       # energy content of somatic tissue at half harvest weight
  dw        <- (anab - catab) / E_somat
  
  data.frame(
    water_temp = water_temp,
    feeding_response = fr,
    feed_ingested = feed_ingested/ref_weight,
    E_assim = E_assim$total, # total energy assimilated
    anabolism = anab, # energy gained from feeding (minus the energy it took to process the feed)
    catabolism = catab,
    metab = anab - catab,
    somatic_energy = E_somat, # energy content of somatic tissue at half harvest weight
    weight_change = dw/ref_weight # weight change at this temperature when at half harvest weight and feed to satiety
  )
}

# Wrapper to use the above function on a raster stack of temperatures instead of a single vector
get_species_responses_r <- function(temp_stack, species_params, feed_params, ref_weight) {
  ncell <- terra::ncell(temp_stack)
  nlyr  <- terra::nlyr(temp_stack)
  temp_vec <- as.vector(terra::values(temp_stack))

  # Only run the model on real temperatures; cells masked outside the EEZ are NA
  ok   <- is.finite(temp_vec)
  resp <- get_species_responses(temp_vec[ok], species_params, feed_params, ref_weight)

  out_cols <- setdiff(names(resp), "water_temp")

  result <- lapply(out_cols, function(col) {
    full <- rep(NA_real_, length(temp_vec))      # scatter results back to full length
    full[ok] <- resp[[col]]
    r <- terra::setValues(temp_stack,            # reuse the stack purely as a geometry template
                          matrix(full, nrow = ncell, ncol = nlyr))
    names(r) <- names(temp_stack)                # keep the date layer names
    r
  })
  names(result) <- out_cols
  result
}
```

```{r metabolic-responses}
#| code-summary: "Calculate metabolic temperature responses for all species"

# nm <- names(parameters_species)[1]
metab_response <- map(
  names(parameters_species),
  function(nm) {
    get_species_responses(
      water_temp = seq(-5, 45, 0.5),
      species_params = parameters_species[[nm]],
      feed_params = parameters_feeds[[nm]],
      ref_weight = unname(parameters_species[[nm]]['CS']/2)
    ) %>% 
    mutate(model_name = nm)
  },
  .progress = T
) %>% 
  setNames(names(parameters_species))
```

```{r plotting-metabolic-responses}
#| code-summary: "Plot and save metabolic response panels for each species"

# metab_df <- metab_response[[1]]
# nm <- names(metab_response)[1]

walk2(
  metab_response,
  names(metab_response),
  function(metab_df, nm) {
    df_proc <- metab_df %>%
      filter(!is.na(feeding_response)) %>% 
      select(-somatic_energy) %>%
      mutate(
        anabolism = anabolism / 1000,
        catabolism = catabolism / 1000,
        metab = metab / 1000,
        E_assim = E_assim / 1000
      )

    plots <- list()

    plots[[1]] <- ggplot(df_proc, aes(x = water_temp, y = feeding_response)) +
        geom_line(linewidth = 0.75) +
        labs(x = NULL, y = "Relative feeding") +
        prettyplot()

    plots[[2]] <- ggplot(df_proc, aes(x = water_temp)) +
        geom_line(aes(y = anabolism), linewidth = 0.75, colour = "steelblue") +
        geom_line(aes(y = catabolism), linewidth = 0.75, colour = "orange") +
        labs(x = NULL, y = "Anabolism/Catabolism (kJ)") +
        prettyplot()

    plots[[3]] <- ggplot(df_proc, aes(x = water_temp, metab)) +
        geom_line(linewidth = 0.75) +
        geom_hline(yintercept = 0, linetype = "dashed", colour = "darkred") +
        labs(x = NULL, y = "Metabolism (kJ)") +
        prettyplot()

    plots[[4]] <- ggplot(df_proc, aes(x = water_temp, E_assim)) +
        geom_line(linewidth = 0.75) +
        labs(x = NULL, y = "Energy assimilated from feed (kJ)") +
        prettyplot()

    plots[[5]] <- ggplot(df_proc, aes(x = water_temp, y = 100*weight_change)) +
        geom_line(linewidth = 0.75) +
        geom_hline(yintercept = 0, linetype = "dashed", colour = "darkred") +
        labs(x = NULL, y = "Weight change (%)") +
        prettyplot()

    combined <- wrap_plots(plots, ncol = 2) +
      plot_annotation(
        title = paste0("Temperature responses of ", nm),
        caption = "Water temperature",
        tag_levels = 'a',
        theme = theme(plot.caption = element_text(hjust = 0.5, size = 11))
      ) &
      theme(
        plot.tag = element_text(size = 11, face = "bold", hjust = 0, vjust = 1),
        plot.tag.location = "panel",
        plot.tag.position = c(0.02, 0.98)
      )

    ggsave(
      file.path(outs_path, "plots", "species_temperature_responses", paste0(nm, ".png")),
      plot = combined,
      width = 8,
      height = 10,
      dpi = 600
    )
  },
  .progress = T
)
```

# Habitat suitability per country/species

```{r temperatures-and-seacells}
#| code-summary: Get all the necessary data

EEZ_by_FAO_full <- file.path(prepdata_path, "EEZ_data_with_FAO_regions.qs") %>%
  qd_read() %>%
  st_transform(crs = 4326) %>%
  st_make_valid()

tos_rast_fnms <- file.path(bigdata_path, "ESGF", "EC-Earth3P-HR", "projected_adjusted") %>% 
  list.files(full.names = T) %>% 
  sort()
tos_dates <- str_extract(basename(tos_rast_fnms), "\\d{4}-\\d{2}-\\d{2}")
keep <- which(month(as.Date(tos_dates)) == 1 & day(as.Date(tos_dates)) == 1 & year(as.Date(tos_dates)) %% 10 == 5) # 2025, 2035, 2045, ...
tos_rast_fnms <- tos_rast_fnms[keep]
tos_dates <- tos_dates[keep]

assigned_farms <- file.path(prepdata_path, "assigned_farms.qs") %>% qs_read()

EEZ_vect <- EEZ_by_FAO_full %>% filter(ISO3_Code == "CHN")
EEZ_vect <- project(vect(EEZ_vect), crs(rast(tos_rast_fnms[1])))
assigned_farms <- assigned_farms %>% filter(ISO3_Code == "CHN")

tos_rasts <- map2(
    tos_rast_fnms,
    tos_dates,
    function(fnm, dt) {
      r <- rast(fnm)
      names(r) <- dt
      crop(r, EEZ_vect, mask = TRUE)
    },
    .progress = T
  )
tos_stack <- rast(tos_rasts)
```

```{r fig-tos-plots}
#| code-summary: Show some example plots of tos changes
#| fig-cap: Sea surface temperature on January 1st over time in the EEZ of China. Points show the location of assigned farms (all species).

# Reproject to lon/lat
tos_decadal <- tos_stack %>% project("EPSG:4326", method = "bilinear")
names(tos_decadal) <- year(as.Date(tos_dates))      # facet strips will show the year

# Make sure farm points are in the right crs
farm_points_sf <- assigned_farms %>% st_transform(4326)

# Plotting function
plot_data_decadal <- function(r, points = NULL, palette = "thermal") {
  e <- as.vector(ext(r))                        # xmin, xmax, ymin, ymax
  e[1] <- e[1] - 0.5
  e[2] <- e[2] + 0.5
  e[3] <- e[3] - 0.5
  e[4] <- e[4] + 0.5

  land <- ne_countries(scale = "large", returnclass = "sf")
  # land <- land[!st_is_empty(land), ]      # drop empty geometries
  # land <- st_make_valid(land)             # fix self-intersections etc.
  # st_agr(land) <- "constant"

  # old_s2 <- sf_use_s2(FALSE)              # planar crop, tolerant of these polygons
  # land <- st_crop(land, c(xmin = e['xmin'] - 0.5, xmax = e['xmax'] + 0.5, ymin = e['ymin'] - 0.5, ymax = e['ymax'] + 0.5))
  # sf_use_s2(old_s2)                       # restore whatever it was before

  fill_scale <- if (palette == "viridis") {
    scale_fill_viridis_c(na.value = "transparent")
  } else {
    scale_fill_gradientn(colours = cmocean(palette)(256), na.value = "transparent")
  }

  p <- ggplot() +
    geom_spatraster(data = r) +
    geom_sf(data = land, fill = "grey85", colour = "grey55", linewidth = 0.2) +
    facet_wrap(~lyr, ncol = 4) +
    fill_scale +
    labs(fill = "SST (°C)", x = "Longitude", y = "Latitude") +
    guides(fill = guide_colourbar(
      theme = theme(
        legend.key.height     = unit(14, "lines"),
        legend.key.width      = unit(0.6, "lines"),
        legend.ticks          = element_line(colour = "white", linewidth = 0.4),
        legend.ticks.length   = unit(0.2, "lines"),
        legend.frame          = element_rect(colour = "grey30", linewidth = 0.3),
        legend.title.position = "top"
      )
    )) +
    theme_classic() +
    theme(
      legend.position = "right",
      legend.title    = element_text(hjust = 0.5)
    )

  if (!is.null(points)) {
    p <- p + geom_sf(data = points, shape = 4, size = 1.5, colour = "black")
  }

  p + coord_sf(xlim = e[1:2], ylim = e[3:4], expand = FALSE)
}

plot_data_decadal(
  r = tos_decadal,
  points = NULL,           # points = farm_points_sf
  palette = "thermal"      # palette = "viridis"
)
```

```{r get-suitability-single-species}
#| code-summary: Get the metabolic suitability for just one species - "grouper"

metab_resps <- get_species_responses_r(
  temp_stack = tos_decadal, 
  species_params = parameters_species[["grouper"]], 
  feed_params = parameters_feeds[["grouper"]], 
  ref_weight = parameters_species[["grouper"]]["CS"]/2
)

farm_points_sf <- farm_points_sf %>% filter(model_name == "grouper")
```

```{r save-metabolic-response-changes}

walk(
  names(metab_resps),
  function(i) {
    p <- plot_data_decadal(
      r = metab_resps[[i]], 
      points = farm_points_sf, 
      palette = "thermal"
    ) + 
      ggtitle(i) +
      labs(fill = i)

    ggsave(
      plot = p, 
      filename = file.path(outs_path, "plots", "metabolic_responses", paste0(i, ".png")),
      height = 10, width = 12
    )
  },
  .progress = T  
)

```

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Choosing species](01_choosing_species.qmd)

[Next: Assigning Locations →](04_assigning_locations.qmd)
:::
