---
title: "4: Extracting future farm temperatures"
subtitle: "FAO Climate Change Risks to Fed Mariculture"
author: 
  - "Tormey Reimer"
date: last-modified
---

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Assigning locations](02_assigning_locations.qmd)

[Next: Test production →](05_00_test_production.qmd)
:::

# Overview {#sec-overview}

```{r setup}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: "Load packages"

library(tidyverse)
library(sf)
library(here)
library(qs2)
library(RColorBrewer)
library(purrr)
library(gt)
library(lpSolve)
library(readxl)
library(janitor)
library(countrycode)
library(tidyterra)
```

```{r source-scripts}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: "Source R scripts in use"

here("src", "dirs.R") %>% source()
here("src", "functions.R") %>% source()
here("src", "display_globals.R") %>% source()
here("src", "mapping_vars.R") %>% source()
```

Once farm locations are assigned, temperatures need to be extracted into the future.

## Correcting temperatures

Bias correction uses the decadal mean from 2015–2024 for both datasets (`data-prep-scripts/correcting-temperatures.R`). The change in temperature per grid cell from the CMIP projections is used as a delta applied on top of the contemporary NASA SST data (i.e. `corrected = CMIP_future − CMIP_meanyear + NASA_meanyear`). February 29 dates in leap years are handled by interpolating the adjacent meanyear layers (DOY 059 and DOY 060) with equal weights. The corrected rasters are saved to `bigdata_path/ESGF/EC-Earth3P-HR/projected_adjusted/`.

```{r projected-adjusted-files}
#| code-summary: List the projected_adjusted files to check we're getting them from the correct place

tos_rast_fnms <- file.path(bigdata_path, "ESGF", "EC-Earth3P-HR", "projected_adjusted") %>% 
  list.files(full.names = T) %>% 
  sort()

# Use just one raster for cell assignment
tos_rast <- rast(tos_rast_fnms[1])
```

# Get farm locations {#sec-get-data}

```{r load-assigned-farm-data}
#| code-summary: Load saved data for summarising

assigned_farms <- file.path(prepdata_path, "assigned_farms.qs") %>% 
  qs_read()
```

## Get farm locations in temperature rasters

Once we have a representative corrected global temperature raster, we can extract the locations we actually want - the farms that have been assigned for use in this analysis. The first step is to assign each farm location a cell number (or several cell numbers) within the temperature raster stack.

```{r farm-cell-extraction}
#| code-summary: Assign cell(s) to each farm and create a lookup table for future temperature extraction

farm_points <- assigned_farms %>% 
  vect()

# Attempt to extract the cell numbers dirrectly underneath assigned farms
farm_cells <- terra::extract(tos_rast, farm_points, cells = T, ID = F) %>% 
  rename(focal_cell = cell)
farm_cells$farm_ID <- farm_points$farm_ID

simple_assigned <- farm_cells %>% 
  filter(!is.na(focal_mean))

message(sprintf("%i of %i farm IDs have a simple cell extracted (%0.1f%%).", 
  nrow(simple_assigned), 
  nrow(farm_cells), 
  100*nrow(simple_assigned)/nrow(farm_cells)
))

# Look at the 4 surrounding cells of each missing cell to try and find a viable temperature
still_missing_1 <- farm_cells %>% 
  filter(is.na(focal_mean))

neighbours_4 <- terra::adjacent(tos_rast, cells = still_missing_1$focal_cell, directions = 4)
neighbours_4 <- split(neighbours_4, row(neighbours_4)) |> unname()

still_missing_1 <- still_missing_1 %>% 
  mutate(neighbours_4 = neighbours_4, new_cells = NA)

still_missing_1 <- still_missing_1 %>%
  mutate(
    new_cells = lapply(neighbours_4, function(nb) {
      cells <- unlist(nb)
      temps <- terra::extract(tos_rast, cells)
      if (any(!is.na(temps$focal_mean))) cells else NA
    })
  )

assigned_4 <- still_missing_1 %>% 
  filter(!is.na(new_cells))

message(sprintf("%i of %i remaining farm IDs have cells from the 4 cardinal directions around extracted (%0.1f%%).", 
  nrow(assigned_4), 
  nrow(still_missing_1), 
  100*nrow(assigned_4)/nrow(still_missing_1))
)

# Look at the 8 surrounding cells of each missing cell to try and find a viable temperature
still_missing_2 <- still_missing_1 %>% 
  filter(is.na(new_cells))

neighbours_8 <- terra::adjacent(tos_rast, cells = still_missing_2$focal_cell, directions = 8)
neighbours_8 <- split(neighbours_8, row(neighbours_8)) |> unname()

still_missing_2 <- still_missing_2 %>% 
  mutate(neighbours_8 = neighbours_8)

still_missing_2 <- still_missing_2 %>%
  mutate(
    new_cells = lapply(neighbours_8, function(nb) {
      cells <- unlist(nb)
      temps <- terra::extract(tos_rast, cells)
      if (any(!is.na(temps$focal_mean))) cells else NA
    })
  )

assigned_8 <- still_missing_2 %>% 
  filter(!is.na(new_cells))

message(sprintf("%i of %i remaining farm IDs have cells from the 8 directions around extracted (%0.1f%%).", 
  nrow(assigned_8), 
  nrow(still_missing_2), 
  100*nrow(assigned_8)/nrow(still_missing_2)
))

# Let's expand the search
still_missing_3 <- still_missing_2 %>% 
  filter(is.na(new_cells))

still_missing_3 <- still_missing_3 %>% 
  mutate(
    new_cells = lapply(neighbours_4, function(nb) {
      nb_all <- terra::adjacent(tos_rast, cells = nb, directions = 8) %>% as.vector() %>% unique()
      nb_all <- terra::adjacent(tos_rast, cells = nb_all, directions = 4) %>% as.vector() %>% unique()
      temps <- terra::extract(tos_rast, nb_all)
      if (any(!is.na(temps$focal_mean))) nb_all else NA
    })
  )

assigned_exp <- still_missing_3 %>% 
  filter(!is.na(new_cells)) 

message(sprintf("%i of %i remaining farm IDs have cells from the expanded cell radius around extracted (%0.1f%%).", 
  nrow(assigned_exp), 
  nrow(still_missing_3), 
  100*nrow(assigned_exp)/nrow(still_missing_3))
)

message(sprintf("There are %i farm_IDs still remaining.", still_missing_3 %>% filter(is.na(new_cells)) %>% nrow()))
```

After 4 rounds of searching progressively wider areas, there are still 137 farms missing temperatures. Where are they?

```{r fig-where-are-the-missing-farms}
#| code-summary: Show the missing farms and their nearest neighbour

missing_farms <- still_missing_3 %>% 
  filter(is.na(new_cells)) %>% 
  pull(farm_ID)

farm_points_missing <- assigned_farms %>% # includes a geometry column
  mutate(is_missing = case_when(farm_ID %in% missing_farms ~ T, T ~ F)) %>% 
  select(farm_ID, is_missing) %>% 
  mutate(type = "missing")

missing <- farm_points_missing %>% filter(is_missing)
non_missing <- farm_points_missing %>% filter(!is_missing)

nearest_idx <- sf::st_nearest_feature(missing, non_missing)
nearst_non_missing <- non_missing[nearest_idx, ] %>% 
  mutate(type = "nonmissing")

paired <- rbind(missing, nearst_non_missing)
duplicated <- cbind(
  st_drop_geometry(missing), 
  nearst_non_missing %>% st_drop_geometry() %>% rename(dup_farm_ID = farm_ID) %>% select(dup_farm_ID)
) %>% 
  select(farm_ID, dup_farm_ID)

ggplot() +
  geom_spatraster(data = tos_rast) +
  geom_sf(data = paired, aes(geometry = geometry, colour = as.factor(type))) +
  scale_fill_viridis_c(na.value = NA) +
  scale_color_manual(values = c("missing" = "black", "nonmissing" = "red")) +
  prettyplot() + coord_sf()
```

The missing farms are mostly in Chile, with a few in Norway. They're generally a little bit inland of the coast (up estuaries, etc) so they're not being well-captured by SST changes. However, they're extremely close to non-missing points of data, so we'll be copying those temperatures for those features.

```{r combine-all-assigned-cells-together}
#| code-summary: Combine cell assignments

# The simple assignments
assigned_farms_cells <- assigned_farms %>% 
  left_join(
    simple_assigned %>% 
      mutate(focal_cells = as.list(focal_cell)) %>% 
      select(focal_cells, farm_ID),
    by = "farm_ID"
  )

# The 4-way assignments
geometry <- sf::st_geometry(assigned_farms_cells) # so annoying
assigned_farms_cells <- assigned_farms_cells %>%
  sf::st_drop_geometry() %>% 
  rows_update(
    assigned_4 %>% 
      select(farm_ID, new_cells) %>% 
      rename(focal_cells = new_cells),
    by = "farm_ID"
  ) %>%
  sf::st_set_geometry(geometry)

# The 8-way assignments
geometry <- sf::st_geometry(assigned_farms_cells) # so annoying
assigned_farms_cells <- assigned_farms_cells %>%
  sf::st_drop_geometry() %>% 
  rows_update(
    assigned_8 %>% 
      select(farm_ID, new_cells) %>% 
      rename(focal_cells = new_cells),
    by = "farm_ID"
  ) %>%
  sf::st_set_geometry(geometry)

# The expanded assignments
geometry <- sf::st_geometry(assigned_farms_cells) # so annoying
assigned_farms_cells <- assigned_farms_cells %>%
  sf::st_drop_geometry() %>% 
  rows_update(
    assigned_exp %>% 
      select(farm_ID, new_cells) %>% 
      rename(focal_cells = new_cells),
    by = "farm_ID"
  ) %>%
  sf::st_set_geometry(geometry)

# The ones copying from neighbours
geometry <- sf::st_geometry(assigned_farms_cells) # so annoying
assigned_farms_cells <- assigned_farms_cells %>% 
  sf::st_drop_geometry() %>% 
  rows_update(
    duplicated %>% mutate(focal_cells = as.list(as.numeric(dup_farm_ID))) %>% select(farm_ID, focal_cells),
    by = "farm_ID"
  ) %>%
  sf::st_set_geometry(geometry)

# Finally check for any missing - should be none!
assigned_farms_cells %>% 
  filter(length(focal_cells) == 0)

qs_save(assigned_farms_cells, file.path(prepdata_path, "assigned_farms_focal_cells.qs"))
```

# Extract future temperatures

```{r extractions-prep}
#| code-summary: Prep for temperature extraction

# quick cleanup
rm(geometry, still_missing_2, still_missing_3, assigned_4, assigned_8, assigned_exp, simple_assigned, farm_points_missing, non_missing, missing, paired, duplicated, still_missing_1, nearst_non_missing)
gc()

# Where to save the final temperature files?
farm_temp_outputs <- file.path(prepdata_path, "assigned_farms_alltemps")
dir.create(farm_temp_outputs, showWarnings = F)

# Group the projected-adjusted temperature raster files by year
tos_rast_fnms_ls <- tibble(
  path = tos_rast_fnms,
  date = as.Date(str_extract(basename(tos_rast_fnms), "\\d{4}-\\d{2}-\\d{2}")),
  year = year(date)
)
tos_rast_fnms_ls <- split(tos_rast_fnms_ls, tos_rast_fnms_ls$year)
```

```{r extract-temps-lookup-cells}
#| code-summary: Extract all farm focal cells for each year, accumulating results into some lookup files
#| eval: false

# Get all focal cells we need to extract for all farms
all_cells <- unique(unlist(assigned_farms_cells$focal_cells))

# yr_fnms <- tos_rast_fnms_ls[[1]]
walk(
  tos_rast_fnms_ls,
  function(yr_fnms) {
    tos_stack <- rast(yr_fnms$path)
    names(tos_stack) <- yr_fnms$date
    
    # Extract ALL cells needed across all farms in one call
    extracted <- terra::extract(tos_stack, all_cells)
    
    # Label rows with cell number and save as a lookup table
    extracted$cell <- all_cells
    qs2::qs_save(
      extracted, 
      file.path(data_path, "intermediates", "farm_focal_lookup_files", paste0("extracted_", unique(yr_fnms$year), ".qs"))
    )
  },
  .progress = T
)
```

```{r per-farm-projected-temperatures}
#| code-summary: Assemble per-farm files from the extracted temperatures in the lookup tables
#| eval: false

assigned_farms_cells <- file.path(prepdata_path, "assigned_farms_focal_cells.qs") %>% qs_read()
subset_farms <- assigned_farms_cells %>% 
  # filter(source == "extracted") %>% 
  pull(farm_ID) %>% unique()

lookup_files <- file.path(data_path, "intermediates", "farm_focal_lookup_files") %>% 
  list.files(pattern = "extracted_\\d{4}\\.qs", full.names = TRUE)

overwrite <- T

# id <- subset_farms[1]
walk(
  subset_farms,
  function(id) {
    out_file <- file.path(farm_temp_outputs, paste0("farm_", fix_int(id, digits = 8), ".qs"))
    if (!file.exists(out_file) | overwrite) {
      cells <- assigned_farms_cells$focal_cells[assigned_farms_cells$farm_ID == id][[1]]
      
      temps <- lookup_files %>% 
        map_dfr(function(fnm) {
          tmp <- qs_read(fnm) %>% 
            filter(cell %in% cells) %>% 
            select(-cell)
          vals <- colMeans(as.matrix(tmp), na.rm = TRUE)
          data.frame(
            date = as.Date(names(tmp)),
            sst = unname(vals)
          )
        }) %>% 
          mutate(farm_ID = id)

      if (any(is.na(temps$sst))) {
        cli::cli_alert_warning(sprintf("Warning! Cell %s has missing temperatures!", id))
      }

      qs2::qs_save(temps, out_file)
    }
  },
  .progress = T
)

# ! Warning! Cell 87416 has missing temperatures!   
# ! Warning! Cell 87479 has missing temperatures!   
# ! Warning! Cell 87520 has missing temperatures!   
# ! Warning! Cell 87521 has missing temperatures!   
# ! Warning! Cell 87525 has missing temperatures!   
```

```{r farm-temperatures-by-model}
#| code-summary: Save farm temperatures by model names - this will make it easier to load for production model loading

model_names <- unique(assigned_farms$model_name)

# mn <- model_names[11]
walk(
  model_names,
  function (mn) {
    model_farms <- assigned_farms %>% 
      filter(model_name == mn)

    temps <- file.path(farm_temp_outputs) %>% 
      list.files(full.names = T) %>% 
      str_subset(paste0(fix_int(model_farms$farm_ID, 8), collapse = "|")) %>% 
      map_dfr(qs_read)

    model_farms <- model_farms %>% 
      left_join(temps, by = join_by(farm_ID)) %>% 
      mutate(year = year(date) %>% as.factor())

    qs2::qs_save(model_farms, file.path(prepdata_path, "farm_temps_bymodel", paste0("farm_temps_", mn, ".qs")))
  },
  .progress = T
)
```

```{r farm-temperatures-per-country}
#| code-summary: Plot farm temperatures by country - mostly just to show how it changes over time

ISO_Codes <- unique(assigned_farms$ISO3_Code)

# iso <- ISO_Codes[11]
walk(
  ISO_Codes,
  function (iso) {
    country_farms <- assigned_farms %>% 
      filter(ISO3_Code == iso)

    temps <- file.path(farm_temp_outputs) %>% 
      list.files(full.names = T) %>% 
      str_subset(paste0(fix_int(country_farms$farm_ID, 8), collapse = "|")) %>% 
      map_dfr(qs_read)

    country_farms <- country_farms %>% 
      left_join(temps, by = join_by(farm_ID)) %>% 
      mutate(year = year(date) %>% as.factor())

    p <- ggplot(country_farms, aes(x = year, y = sst, fill = model_name)) +
      geom_boxplot() +
      theme_classic() +
      facet_wrap(~model_name, ncol = 1) +
      theme(axis.text.x = element_text(angle = 90))

    ggsave(
      plot = p,
      filename = file.path(outs_path, "plots", "farm_temperatures", paste0("farm_temps_", iso, ".png")),
      dpi = 300,
      width = 10,
      height = 2.5 * max(ggplot_build(p)$layout$layout$ROW) + 1
    )
  },
  .progress = T
)
```

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Assigning locations](02_assigning_locations.qmd)

[Next: Test production →](05_00_test_production.qmd)
:::
