---
title: "5.2: Consolidate results"
subtitle: "FAO Climate Change Risks to Fed Mariculture"
author: 
  - "Tormey Reimer"
date: last-modified
---

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Testing production](05_01_run_production.qmd)

[Next: Home →](../index.qmd)
:::

# Overview {#sec-overview}

```{r setup}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false

library(tidyverse)
library(here)
library(janitor)
library(qs2)
library(units)

remove_unit("g_fish")
remove_unit("kg_fish")
remove_unit("t_fish")

install_unit("g_fish")
install_unit("kg_fish", "1000 g_fish")
install_unit("t_fish", "1000 kg_fish")
```

```{r source-scripts}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: "Source R scripts in use"

here("src", "dirs.R") %>% source()
here("src", "functions.R") %>% source()
here("src", "model_functions.R") %>% source()
```

This document checks that the future production runs are complete and consolidates them into more useable forms.

# Check production files

First check that all the files in the folder are complete.

```{r check-production}
#| code-summary: Check that the files in the production folder are complete and correct structure

prod_path <- file.path(outs_path, "data", "farm_production")
production_files <- list.files(prod_path, full.names = TRUE, recursive = T, pattern = "MC5000\\.qs$")

# here("src", "check_production_files.R") %>% source(echo = T)
```

And display how many farms are present/missing.

```{r check-farm-production-missing}
#| code-summary: Check what files have been done

farms_done <- as.integer(str_extract(basename(production_files), "(?<=farmID_)\\d+"))

assigned_farms <- file.path(prepdata_path, "assigned_farms.qs") %>% 
  qs_read() %>% 
  sf::st_drop_geometry() %>% 
  mutate(done = case_when(farm_ID %in% farms_done ~ T, T ~ F))

# Pair assigned farms with feed assignment data
feed_assignments <- file.path(rawdata_path, "feed_profiles_and_composition.xlsx") %>% 
  read_excel(sheet = "feed_assignments") %>% 
  select(model_name, country, feed_class)

assigned_farms <- assigned_farms %>% 
  left_join(feed_assignments, by = join_by(model_name, country))

assigned_farms %>% 
  group_by(model_name, feed_class, done) %>% 
  reframe(n = n()) %>% 
  # filter(model_name %in% c("atlantic_salmon", "rainbow_trout", "seabream")) %>% 
  filter(!is.na(feed_class)) %>% 
  arrange(model_name, -done)
```

# Per-farm plots

These plots aren't meant to show anything specifically - they're just so that I can quickly flick through the pictures and see if anything has gone awry with the production modelling. For that reason, there are only three plots saved for each farm:

* Total farm production
* Total feed ingested
* Feed per biomass (essentially FCR)

```{r save-plots-per-farm}
#| code-summary: Save some diagnostic plots per farm
#| eval: false

fb_path <- file.path(outs_path, "plots", "farm_production_checks", "farm_biomass")
fr_path <- file.path(outs_path, "plots", "farm_production_checks", "feed_required")
frb_path <- file.path(outs_path, "plots", "farm_production_checks", "feed_required_per_biomass")

# Choose a subset
prod_files_subset <- production_files
# prod_files_subset <- production_files[farms_done %in% assigned_farms$farm_ID[assigned_farms$model_name == "rainbow_trout" & assigned_farms$feed_class == "world"]]

walk(prod_files_subset, function(fnm) {
  prod_ls <- qs_read(fnm)
  farm_ID <- str_extract(basename(fnm), "(?<=farmID_)\\d+")

  fb_fnm <- file.path(fb_path, paste0("harvested_biomass_farmID_", farm_ID, ".png"))
  fr_fnm <- file.path(fr_path, paste0("feed_required_farmID_", farm_ID, ".png"))
  frb_fnm <- file.path(frb_path, paste0("feed_required_perbiomass_farmID_", farm_ID, ".png"))
  
  if(any(c(!file.exists(fb_fnm), !file.exists(fr_fnm), !file.exists(frb_fnm)))) {
    fb <- tidy_stat(prod_ls, "weight_scaled") %>% 
      slice_max(prod_day) %>% 
      mutate(
        mean = mean %>% set_units("g") %>% set_units("t"),
        sd = sd %>% set_units("g") %>% set_units("t")
      ) %>% 
      select(-prod_day, -day)

    fr <- tidy_stat(prod_ls, "ing_act_scaled") %>% 
      group_by(year) %>% 
      reframe(
        mean = sumna(mean),
        sd = sqrt(sumna(sd^2))
      ) %>% 
      mutate(
        mean = mean %>% set_units("g") %>% set_units("t"),
        sd = sd %>% set_units("g") %>% set_units("t")
      )

    p_fb <- fb %>% 
      ggplot(aes(x = year, y = mean, ymin = mean - sd, ymax = mean + sd)) +
      geom_line() +
      geom_ribbon(fill = "salmon", alpha = 0.35) +
      scale_x_continuous(breaks = seq(2030, 2100, 10)) +
      theme_classic() +
      labs(
        title = paste0("Farm ", as.integer(farm_ID), ": harvested biomass"),
        x = "Year",
        y = "Biomass"
      )
    ggsave(
      fb_fnm, 
      plot = p_fb, 
      height = 8,
      width = 10
    )

    p_fr <- fr %>% 
      ggplot(aes(x = year, y = mean, ymin = mean - sd, ymax = mean + sd)) +
      geom_line() +
      geom_ribbon(fill = "salmon", alpha = 0.35) +
      scale_x_continuous(breaks = seq(2030, 2100, 10)) +
      theme_classic() +
      labs(
        title = paste0("Farm ", as.integer(farm_ID), ": feed required"),
        x = "Year",
        y = "Feed"
      )
    ggsave(
      fr_fnm, 
      plot = p_fr, 
      height = 8,
      width = 10
    )

    frb <- left_join(fb, fr, by = join_by(year)) %>% 
      mutate(
        mean.y = set_units(mean.y, "kg"),
        mean.x = mean.x %>% drop_units() %>% set_units("t_fish"),
        mean = mean.y/mean.x,
        sd = mean * sqrt((drop_units(sd.y)/drop_units(mean.y))^2 + (drop_units(sd.x)/drop_units(mean.x))^2),
        FCR = mean %>% set_units("t t_fish-1") %>% drop_units()
      )
    p_frb <- frb %>% 
      ggplot(aes(x = year, y = mean, ymin = mean - sd, ymax = mean + sd)) +
      geom_line() +
      geom_ribbon(fill = "salmon", alpha = 0.35) +
      scale_x_continuous(breaks = seq(2030, 2100, 10)) +
      theme_classic() +
      labs(
        title = paste0("Farm ", as.integer(farm_ID), ": feed required per biomass"),
        x = "Year",
        y = "Feed required"
      )
    ggsave(
      frb_fnm, 
      plot = p_frb, 
      height = 8,
      width = 10
    )
  }
},
.progress = T
)
```

# Group and save {#sec-group-save}

| model_name         | feed_class  | production done | production waiting | consolidation done |
|--------------------|-------------|-----------------|--------------------|--------------------|
| asian_seabass      | china       | 235             | 0                  | Y                  |
| atlantic_salmon    | chile       | 1495            | 0                  | Y                  |
| atlantic_salmon    | norway      | 915             | 0                  | Y                  |
| atlantic_salmon    | uk          | 278             | 0                  | Y                  |
| atlantic_salmon    | canada      | 0               | 230                |                    |
| european_seabass   | europe      | 50              | 421                |                    |
| golden_pompano     | china       | 0               | 253                |                    |
| milkfish           | philippines | 0               | 746                |                    |
| rainbow_trout      | chile       | 335             | 0                  | Y                  |
| rainbow_trout      | norway      | 342             | 0                  | Y                  |
| rainbow_trout      | world       | 107             | 0                  | Y                  |
| seabream           | china       | 239             | 0                  | Y                  |
| seabream           | europe      | 252             | 0                  | Y                  |
| whiteleg_shrimp    | china       | 0               | 1230               |                    |
| whiteleg_shrimp    | ecuador     | 0               | 2147               |                    |
| whiteleg_shrimp    | india       | 0               | 1226               |                    |
| whiteleg_shrimp    | indonesia   | 0               | 1521               |                    |

```{r subset}
#| code-summary: Subset results

# Check what stats you have to work with
qs_read(production_files[1])[[1]] %>% str()

subset_farms <- assigned_farms %>% 
  filter(model_name == "seabream" & feed_class == "europe")

subset_prod_files <- production_files[which(as.integer(str_extract(basename(production_files), "(?<=farmID_)\\d+")) %in% subset_farms$farm_ID)]

cons_path <- file.path(outs_path, "data", "consolidated")
dir.create(cons_path, showWarnings = F)
```

```{r farm-biomass}
#| code-summary: Save farm biomass results per species/feed type

weight_scaled <- map_dfr(
  subset_prod_files,
  function(fnm) {
    tidy_stat(qs_read(fnm), "weight_scaled") %>% 
      mutate(farm_ID = as.integer(str_extract(basename(fnm), "(?<=farmID_)\\d+"))) %>% 
      slice_max(prod_day) %>% 
      rename(farm_mean = mean, farm_sd = sd) %>% 
      select(-day, -prod_day)
  },
  .progress = T
)

weight_scaled <- assigned_farms %>% 
  right_join(weight_scaled, by = join_by(farm_ID))

weight_scaled_2025 <- weight_scaled %>% 
  filter(year == 2025) %>% 
  select(farm_ID, mean_2025 = farm_mean)
# max(weight_scaled_2025$error)

weight_scaled <- weight_scaled %>% 
  right_join(weight_scaled_2025, by = join_by(farm_ID)) %>% 
  group_by(ISO3_Code, country, F_CODE, model_name, feed_class, year) %>% 
  reframe(
    mean_2025 = sum(mean_2025),
    n_farms = n(),
    mean = sum(farm_mean),
    sd = sqrt(sumna(farm_sd^2))
  )

qs_save(
  weight_scaled, 
  file.path(cons_path, paste0("weight_scaled-", unique(weight_scaled$model_name), "-", unique(weight_scaled$feed_class), ".qs"))
  )
```

```{r feed-demand}
#| code-summary: Save feed demand results per species/feed type

ing_act_scaled <- map_dfr(
  subset_prod_files,
  function(fnm) {
    tidy_stat(qs_read(fnm), "ing_act_scaled") %>% 
      mutate(farm_ID = as.integer(str_extract(basename(fnm), "(?<=farmID_)\\d+"))) %>% 
      group_by(farm_ID, year) %>% 
      reframe(
        farm_mean = sumna(mean),
        farm_sd = sqrt(sumna(sd^2))
      )
  },
  .progress = T
)

ing_act_scaled <- assigned_farms %>% 
  right_join(ing_act_scaled, by = join_by(farm_ID)) 

ing_act_scaled_2025 <- ing_act_scaled %>% 
  filter(year == 2025) %>% 
  select(farm_ID, mean_2025 = farm_mean)

ing_act_scaled <- ing_act_scaled %>% 
  right_join(ing_act_scaled_2025, by = join_by(farm_ID)) %>% 
  group_by(ISO3_Code, country, F_CODE, model_name, feed_class, year) %>% 
  reframe(
    mean_2025 = sumna(mean_2025),
    n_farms = n(),
    mean = sumna(farm_mean),
    sd = sqrt(sumna(farm_sd^2))
  )

qs_save(
  ing_act_scaled, 
  file.path(cons_path, paste0("ing_act_scaled-", unique(ing_act_scaled$model_name), "-", unique(ing_act_scaled$feed_class), ".qs"))
  )
```

```{r feed-provided}
#| code-summary: Save feed provided results per species/feed type

food_prov_scaled <- map_dfr(
  subset_prod_files,
  function(fnm) {
    tidy_stat(qs_read(fnm), "food_prov_scaled") %>% 
      mutate(farm_ID = as.integer(str_extract(basename(fnm), "(?<=farmID_)\\d+"))) %>% 
      group_by(farm_ID, year) %>% 
      reframe(
        farm_mean = sumna(mean),
        farm_sd = sqrt(sumna(sd^2))
      )
  },
  .progress = T
)

food_prov_scaled <- assigned_farms %>% 
  right_join(food_prov_scaled, by = join_by(farm_ID)) 

food_prov_scaled_2025 <- food_prov_scaled %>% 
  filter(year == 2025) %>% 
  select(farm_ID, mean_2025 = farm_mean)

food_prov_scaled <- food_prov_scaled %>% 
  right_join(food_prov_scaled_2025, by = join_by(farm_ID)) %>% 
  group_by(ISO3_Code, country, F_CODE, model_name, feed_class, year) %>% 
  reframe(
    mean_2025 = sumna(mean_2025),
    n_farms = n(),
    mean = sumna(farm_mean),
    sd = sqrt(sumna(farm_sd^2))
  )

qs_save(
  food_prov_scaled, 
  file.path(cons_path, paste0("food_prov_scaled-", unique(ing_act_scaled$model_name), "-", unique(ing_act_scaled$feed_class), ".qs"))
  )
```

```{r ingestion-per-biomass}
#| code-summary: Save feed ingested per biomass results per species/feed type

ingest_biomass <- left_join(
  ing_act_scaled %>% rename(ing_act_2025 = mean_2025, ing_act_mean = mean, ing_act_sd = sd), 
  weight_scaled %>% rename(weight_2025 = mean_2025, weight_mean = mean, weight_sd = sd),
  by = join_by(ISO3_Code, country, F_CODE, model_name, feed_class, year, n_farms)
)

ingest_biomass <- ingest_biomass %>% 
  mutate(
    ingest_biomass_2025 = ing_act_2025/weight_2025,
    ingest_biomass_mean = ing_act_mean/weight_mean,
    ingest_biomass_sd = ingest_biomass_mean * sqrt((ing_act_sd/ing_act_mean)^2 + (weight_sd/weight_mean)^2)
  ) %>% 
    select(-c(ing_act_2025, weight_2025, ing_act_mean, weight_mean, ing_act_sd, weight_sd))

qs_save(
  ingest_biomass, 
  file.path(cons_path, paste0("ingest_biomass-", unique(ingest_biomass$model_name), "-", unique(ingest_biomass$feed_class), ".qs"))
  )
```

```{r feed-prov-per-biomass}
#| code-summary: Save feed provided per biomass results per species/feed type

feedprov_biomass <- left_join(
  food_prov_scaled %>% rename(food_prov_2025 = mean_2025, food_prov_mean = mean, food_prov_sd = sd), 
  weight_scaled %>% rename(weight_2025 = mean_2025, weight_mean = mean, weight_sd = sd),
  by = join_by(ISO3_Code, country, F_CODE, model_name, feed_class, year, n_farms)
)

feedprov_biomass <- feedprov_biomass %>% 
  mutate(
    feedprov_biomass_2025 = food_prov_2025/weight_2025,
    feedprov_biomass_mean = food_prov_mean/weight_mean,
    feedprov_biomass_sd = feedprov_biomass_mean * sqrt((food_prov_sd/food_prov_mean)^2 + (weight_sd/weight_mean)^2)
  ) %>% 
    select(-c(food_prov_2025, weight_2025, food_prov_mean, weight_mean, food_prov_sd, weight_sd))

qs_save(
  feedprov_biomass, 
  file.path(cons_path, paste0("feedprov_biomass-", unique(feedprov_biomass$model_name), "-", unique(feedprov_biomass$feed_class), ".qs"))
  )
```

```{r}

```

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Testing production](05_00_test_production.qmd)

[Next: Home →](../index.qmd)
:::
