---
title: "5.1: Run future production"
subtitle: "FAO Climate Change Risks to Fed Mariculture"
author: 
  - "Tormey Reimer"
date: last-modified
---

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Testing production](05_00_test_production.qmd)

[Next: Home →](../index.qmd)
:::

# Overview {#sec-overview}

```{r setup}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false

library(furrr)
library(future)
library(tidyverse)
library(here)
library(readxl)
library(janitor)
library(lhs)
# library(scales)
library(qs2)
library(slider)
library(units)
```

```{r source-scripts}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: "Source R scripts in use"

here("src", "dirs.R") %>% source()
here("src", "model_functions.R") %>% source()
here("src", "other_functions.R") %>% source()
```

This document runs the future production for all models across all farms for the years 2025-2099.

# Species and feed parameters {#sec-species-params}

```{r species-parameters}
#| code-summary: Load species parameters

species_params <- file.path(prepdata_path, "species_parameters") %>% 
  list.files(full.names = T)

model_names <- species_params %>% 
  basename() %>% 
  str_remove_all(".qs|species_parameters_")

species_params <- map(species_params, qd_read) %>% 
  setNames(model_names)
```

Load the feeds still stored in the raw data and store them as feed objects.

```{r feed-params}
#| code-summary: Load feed parameters and save one per model_name/feed assignment

# Get raw data
raw_feed_data <- file.path(rawdata_path, "feed_profiles_and_composition.xlsx") %>% 
  read_excel(sheet = "feed_formulations") %>% 
  select(feed, ingredient, proportion)

ingredients_df <- file.path(rawdata_path, "all_ingredients.xlsx") %>% 
  read_excel(sheet = "all_ingredients") %>% 
  select(ingredient, protein, lipid, carb)

digestibility_df <- file.path(rawdata_path, "all_ingredients.xlsx") %>% 
  read_excel(sheet = "all_ingredients") %>% 
  clean_names() %>% 
  rename(
    protein_digestibility = mean_protein_digestibility, 
    lipid_digestibility = mean_lipid_digestibility, 
    carb_digestibility = mean_carb_digestibility
  ) %>% 
  select(ingredient, protein_digestibility, lipid_digestibility, carb_digestibility)

# Combine feed and ingredient data and save as feed objects
feeds_for_now <- unique(raw_feed_data$feed)
feeds_for_now <- feeds_for_now[str_detect(feeds_for_now, "-")]
for (f in feeds_for_now) {
  feed_data <- sum_feeds(
    format_feeds(raw_feed_data %>% filter(feed == f), ingredients_df, digestibility_df)
    )[[1]]
  qs_save(feed_data, file.path(prepdata_path, "feed_parameters", paste0(f, ".qs")))
}
```

```{r load-feeds}
#| code-summary: Load the feeds in with their model_name-country names

feed_params <- file.path(prepdata_path, "feed_parameters") %>% 
  list.files(full.names = T)

feed_names <- feed_params %>% 
  basename() %>% 
  str_remove_all(".qs")

feed_params <- map(feed_params, qs_read) %>% 
  setNames(feed_names)
```

# Farm temperatures {#sec-farm-temperatures}

The "assigned farms" table acts as a guide for the production run. It specifies which temperature timeseries to use (via farm_ID) and which species to grow there.

```{r get-assigned-farms}

assigned_farms <- file.path(prepdata_path, "assigned_farms.qs") %>% 
  qs_read() %>% 
  sf::st_drop_geometry()

farm_temp_files <- file.path(prepdata_path, "assigned_farms_alltemps") %>% 
  list.files(full.names = T)
farm_temp_file_IDs <- farm_temp_files %>% 
  basename() %>% 
  str_remove_all(".qs|farm_") %>% 
  as.integer()

farm_temp_files <- data.frame(
  farm_ID = farm_temp_file_IDs,
  filename = farm_temp_files
)

assigned_farms <- assigned_farms %>% 
  left_join(farm_temp_files, by = "farm_ID")

# Any missing?
assigned_farms %>% filter(is.na(filename))
```

# CHOOSE SUBSET for this run

```{r choose-subset}
#| code-summary: Choose the current subset of farms we're working with

# Pair assigned farms with feed assignment data
feed_assignments <- file.path(rawdata_path, "feed_profiles_and_composition.xlsx") %>% 
  read_excel(sheet = "feed_assignments") %>% 
  select(model_name, country, feed_class)

assigned_farms <- assigned_farms %>% 
  left_join(feed_assignments, by = join_by(model_name, country)) %>% 
  filter(!is.na(feed_class)) %>% 
  mutate(feed_name = paste(model_name, feed_class, sep = "-"))

# Choose what subset you're going to run
assigned_farms <- assigned_farms %>% 
  filter(feed_name %in% c("whiteleg_shrimp-ecuador"))

assigned_farms <- split(assigned_farms, assigned_farms$farm_ID)
```

Before running production, we need to establish the following per-farm parameters:

* Grow times (day of start/harvest) - these will be based on 2025 temeprature timeseries
* Farm population (scaling factor) - based on 2025 temperatures and harvest sizes, and per-farm production

```{r helper-functions}

# Get the best "growing window" for this species
get_growing_window <- function(temperatures, grow_days, species_params) {
  temperatures$fr <- sapply(
    X = temperatures$sst, 
    FUN = feeding_rate, 
    species_params = species_params
  )
  temperatures$fr[is.na(temperatures$fr)] <- 0

  temperatures %>% 
    mutate(roll_fr = slide_dbl(fr, sum, .before = 0, .after = grow_days - 1)) %>%
    slice_max(roll_fr, n = 1) %>%
    mutate(end_doy = doy + grow_days - 1) %>% 
    select(start = doy, end = end_doy)
}
```

```{r set-per-farm-parameters}
#| code-summary: Set the grow-times and get the representative harvest size for each farm

# af <- assigned_farms[[12]]
assigned_farms <- map(
  assigned_farms,
  function(af) {
    species <- af$model_name
    sp <- species_params[[species]]
    fp <- feed_params[[af$feed_name]]
    gd <- sp[["gd"]] %>% as.integer()

    # Get the base temperatures for this farm
    temp_2025 <- af$filename %>% 
      qs_read() %>% 
      filter(year(date) == 2025) %>% 
      mutate(doy = as.integer(format(date, "%j")))

    # Repeat the base year (2025) to set growing conditions
    temp_2025 <- rbind(
      temp_2025,
      temp_2025 %>% mutate(doy = doy + 365),
      temp_2025 %>% mutate(doy = doy + 730)
    )

    doys <- get_growing_window(
      temperatures = temp_2025,
      grow_days = gd,
      species_params = sp
      ) %>% 
      slice_head(n = 1)

    # Narrow down the temperature timeseries to only the growing days
    temp_base <- temp_2025 %>% 
      filter(doy >= doys$start & doy <= doys$end) %>% 
      pull(sst)

    # Grow a representative individual fish with this timeseries
    rep_ind <- fish_growth(
      species_params = sp, 
      water_temp = temp_base, 
      feed_params = fp, 
      times = c(t_start = doys$start, t_end = doys$end, dt = 1L), 
      init_weight = sp[["meanW"]], 
      ingmax = sp[["meanImax"]], 
      output_vars = c("weight")
    )
    rep_ind <- unname(rep_ind[nrow(rep_ind), 2]) # get harvest weight (g)

    # Get scaling factor from harvest weight (g) and per-farm production (t)
    pop <- (af$prod_perfarm * 10^6)/rep_ind

    # At the end, give the start and end days, the individual harvest size, and the final population (scaling factor)
    af %>% 
      mutate(
        start_doy = doys$start,
        end_doy = doys$end,
        harvest_size = rep_ind,
        final_pop = pop
      )
  },
  .progress = T
)
```

```{r check-2025}
#| code-summary: Check that the 2025 (per-farm) parameters make sense

assigned_farms_df <- bind_rows(assigned_farms) %>% 
  filter(farm_ID != 00008994)

ggplot(assigned_farms_df, aes(
    x = start_doy, 
    # y = after_stat(ncount)*100, 
    fill = country, colour = country
  )) +
  geom_histogram(alpha = 0.5, position = "identity") +
  # scale_colour_brewer(palette = "Set1") +
  # scale_fill_brewer(palette = "Set1") +
  prettyplot() +
  facet_wrap(~country, scales = "free") +
  labs(title = "Start DOY")

ggplot(assigned_farms_df, aes(
    x = harvest_size, 
    # y = after_stat(ncount)*100, 
    fill = country, colour = country
  )) +
  geom_histogram(alpha = 0.5, position = "identity") +
  # scale_colour_brewer(palette = "Set1") +
  # scale_fill_brewer(palette = "Set1") +
  prettyplot() +
  facet_wrap(~country, scales = "free") +
  labs(title = "Representative farm harvest size")

ggplot(assigned_farms_df, aes(
    x = final_pop, 
    # y = after_stat(ncount)*100, 
    fill = country, colour = country
  )) +
  geom_histogram(alpha = 0.5, position = "identity") +
  # scale_colour_brewer(palette = "Set1") +
  # scale_fill_brewer(palette = "Set1") +
  prettyplot() +
  facet_wrap(~country, scales = "free") +
  labs(title = "Farm population (scaling factor)")
```

# Run production

There are several important metrics to get out of this process. At each farm and in each year, we need to show:

1. The total biomass produced (we're not adjusting the farm scaling factor/population for now)
2. The total feed provided/consumed by the fish (`feed_prov`). `ing_act` is also outputted in case post-hoc changes need to be made to the feeding efficiency parameter.
3. Some metabolic parameters - these aren't completely necessary, more of an explanatory variable for the previous two outputs.

```{r prep-production}
#| code-summary: Prep for the main production and save the outputs at each farm

# These are the variables that will be reported from the growth model at the fish level (mean across the farm +- SD)
# "days" is always included in the output variables
output_vars <- c("weight", "dw", "T_response", "rel_feeding", "food_prov", "ing_act", "anab", "catab", "total_excr", "metab")
# These are the variables that will be scaled up to give farm-level responses
scaled_vars <- c("weight", "dw", "ing_act", "total_excr", "food_prov")

# Folders for results
prod_path_1 <- file.path(outs_path, "data", "farm_production")
prod_path_2 <- file.path(outs_path, "data", "farm_production", "new_local")

harvest_years <- 2025:2099      # Leave this - all harvest years are included in the same file per farms
MC_pop <- 5000                  # Size of the Monte-Carlo-sampled population

farm_IDs <- map(assigned_farms, function(af) {af$farm_ID}) |> unlist() |> unname()
prod_files_1 <- file.path(prod_path_1, paste0("production_results_farmID_", fix_int(farm_IDs, 8), "_MC", MC_pop, ".qs"))
prod_files_2 <- file.path(prod_path_2, paste0("production_results_farmID_", fix_int(farm_IDs, 8), "_MC", MC_pop, ".qs"))

# Figure out which files you need to do
files_to_do <- intersect(which(!file.exists(prod_files_1)), which(!file.exists(prod_files_2)))
# files_to_do <- sample(files_to_do, 10)

sprintf("%s: %d", assigned_farms[[files_to_do[1]]]$feed_name, length(files_to_do))
```

```{r check-farm-growth}
#| code-summary: Check that the parameters are suitable for the full farm growth (2025 only)
#| eval: false

af <- assigned_farms[[files_to_do[1]]]

species <- af$model_name
sp <- species_params[[species]]
fp <- feed_params[[af$feed_name]]
gd <- sp[["gd"]] %>% as.integer()

# Get all temperatures at this farm
temps_all <- af$filename %>% 
  qs_read() %>% 
  mutate(
    doy = as.integer(format(date, "%j")),
    year = year(date)
  ) %>% 
  select(-date)

# Fill in 2024 to reconcile multi-year growing periods
temps_all <- rbind(
  temps_all %>% filter(year == 2025) %>% mutate(year = 2024),
  temps_all
)

# Get correct species growtimes
grow_times <- c(
  t_start = af$start_doy,
  t_end = af$end_doy,
  dt = 1L
)

# Filter to actual growing window for each harvest year
# The previous year is added so that the harvest happens IN the year specified
# yr <- 2025
temps_all <- map(
  harvest_years,
  function(yr) {
    if (grow_times[["t_end"]] > 365) {
      temp <- temps_all %>% filter(year %in% c(yr, yr-1))
      temp$doy <- 1:nrow(temp)
    } else {
      temp <- temps_all %>% filter(year == yr)
    }
    temp %>% 
      filter(doy >= grow_times[["t_start"]] & doy <= grow_times[["t_end"]]) %>% 
      mutate(act_year = year, year  = yr)
  }
) %>% 
  setNames(harvest_years)

# Generate the population (scaling factor)
pop <- generate_pop(harvest_n = af$final_pop, mort = sp[["mortmyt"]], times = grow_times)

check_farm_growth_inputs(
  species_params = sp, 
  feed_params = fp, 
  water_temp = temps_all[[1]]$sst, 
  times = grow_times,
  N_pop = pop, 
  use_MC_population = T, 
  MC_pop = MC_pop,
  output_vars = output_vars,
  scaled_vars = scaled_vars
)
```

```{r estimate-runtime}
#| code-summary: Estimate the total runtime for the missing files using 2% MC population
#| eval: false

af <- assigned_farms[[files_to_do[1]]]
fnm <- prod_files_2[files_to_do[1]]
species <- af$model_name
sp <- species_params[[species]]
fp <- feed_params[[af$feed_name]]
gd <- sp[["gd"]] %>% as.integer()

# Get all temperatures at this farm
temps_all <- af$filename %>% 
  qs_read() %>% 
  mutate(
    doy = as.integer(format(date, "%j")),
    year = year(date)
  ) %>% 
  select(-date)

# Fill in 2024 and 2100 to reconcile multi-year growing periods
temps_all <- rbind(
  temps_all %>% filter(year == 2025) %>% mutate(year = 2024),
  temps_all,
  temps_all %>% filter(year == 2099) %>% mutate(year = 2100)
) %>% 
  arrange(year, doy)

# Get correct species growtimes
end_gd <- if (af$end_doy > 365) {af$end_doy - 365} else {af$end_doy} # this should be in the harvest year
grow_times <- c(
  t_start = af$start_doy,
  t_end = af$end_doy,
  dt = 1L
)

# Filter to actual growing window for each harvest year
# yr <- 2025
temps_all <- map(
  harvest_years,
  function(yr) {
    temp <- temps_all %>% 
      filter(year %in% c(yr, yr-1, yr+1))
    temp$doy <- 1:nrow(temp)
    temp %>% 
      filter(doy >= grow_times[["t_start"]] & doy <= grow_times[["t_end"]]) %>% 
      mutate(year  = yr)
  }
) %>% 
  setNames(harvest_years)

# Generate the population (scaling factor)
pop <- generate_pop(harvest_n = af$final_pop, mort = sp[["mortmyt"]], times = grow_times)

start_time <- Sys.time()

# Run the full production
# temps <- temps_all[[1]]
# yr <- harvest_years[1]
fg <- map2(
  temps_all,
  harvest_years,
  function(temps, yr) {
    farm_growth(
      species_params = sp, 
      feed_params = fp, 
      water_temp = temps$sst, 
      times = grow_times,
      N_pop = pop, 
      use_MC_population = T, 
      MC_pop = 100, # 2% of total
      output_vars = output_vars,
      scaled_vars = scaled_vars
    )
  },
  .progress = T
)

end_time <- Sys.time()
single_time <- (end_time - start_time)*50
total_time <- single_time * length(files_to_do)
cores <- 20

# approx time to do one file
sprintf("One file: %0.0f minutes, or %0.1f hours", single_time, single_time/60)

# approx time to do all files, using 20 cores
sprintf(
  "All files, %d cores: %0.0f minutes, or %0.1f hours, or %0.1f days", 
  cores,
  as.numeric(total_time/cores), 
  as.numeric(total_time/cores/60), 
  as.numeric(total_time/cores/60/24)
)
```

``` {r run-production}
#| code-summary: Run the main production and save the outputs at each farm
#| eval: false

work_cores <- parallelly::availableCores() - 2
plan(multisession, workers = work_cores)

tictoc::tic()

# af <- assigned_farms[[files_to_do[1]]]
# fnm <- prod_files_2[[files_to_do[1]]]
future_walk2(
  assigned_farms[files_to_do],
  prod_files_2[files_to_do],
  function(af, fnm) {
    species <- af$model_name
    sp <- species_params[[species]]
    fp <- feed_params[[af$feed_name]]
    gd <- sp[["gd"]] %>% as.integer()

    # Get all temperatures at this farm
    temps_all <- af$filename %>% 
      qs_read() %>% 
      mutate(
        doy = as.integer(format(date, "%j")),
        year = year(date)
      ) %>% 
      select(-date)

    # Fill in 2024 to reconcile multi-year growing periods
    temps_all <- rbind(
      temps_all %>% filter(year == 2025) %>% mutate(year = 2024),
      temps_all
    )

    # Get correct species growtimes
    grow_times <- c(
      t_start = af$start_doy,
      t_end = af$end_doy,
      dt = 1L
    )

    # Filter to actual growing window for each harvest year
    # The previous year is added so that the harvest happens IN the year specified
    # yr <- 2025
    temps_all <- map(
      harvest_years,
      function(yr) {
        if (grow_times[["t_end"]] > 365) {
          temp <- temps_all %>% filter(year %in% c(yr, yr-1))
          temp$doy <- 1:nrow(temp)
        } else {
          temp <- temps_all %>% filter(year == yr)
        }
        temp %>% 
          filter(doy >= grow_times[["t_start"]] & doy <= grow_times[["t_end"]]) %>% 
          mutate(act_year = year, year  = yr)
      }
    ) %>% 
      setNames(harvest_years)

    # Generate the population (scaling factor)
    pop <- generate_pop(harvest_n = af$final_pop, mort = sp[["mortmyt"]], times = grow_times)

    # Run the full production
    # temps <- temps_all[[2]]
    # yr <- harvest_years[2]
    fg <- map2(
      temps_all,
      harvest_years,
      function(temps, yr) {
        farm_growth(
          species_params = sp, 
          feed_params = fp, 
          water_temp = temps$sst, 
          times = grow_times,
          N_pop = pop, 
          use_MC_population = T, 
          MC_pop = MC_pop,
          output_vars = output_vars,
          scaled_vars = scaled_vars
        )
      }
    )

    qs2::qs_save(fg, fnm)

  },
  .options = furrr_options(seed = TRUE),
  .progress = T
)

plan(sequential)

message(sprintf("%i files done", length(files_to_do)))
tictoc::toc()
```

Check the production files directory to make sure they ran and saved correctly.

```{r check-production}
prod_path <- file.path(outs_path, "data", "farm_production", "new_remote")
production_files <- list.files(prod_path, full.names = TRUE, pattern = "MC5000\\.qs$")

here("src", "check_production_files.R") %>% source(echo = T)

production_files_2 <- file.path(outs_path, "data", "farm_production", basename(production_files))
file.rename(production_files, production_files_2)
```

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Testing production](05_00_test_production.qmd)

[Next: Home →](../index.qmd)
:::
