---
title: "6: Explore production"
subtitle: "FAO Climate Change Risks to Fed Mariculture"
author: 
  - "Tormey Reimer"
date: last-modified
---

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Run production](05_01_run_production_seabream.qmd)

[Next: Home →](../index.qmd)
:::

# Overview {#sec-overview}

```{r setup}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false

library(tidyverse)
library(here)
library(janitor)
library(scales)
library(gt)
library(qs2)
library(units)
```

```{r source-scripts}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: Source R scripts in use

here("src", "dirs.R") %>% source()
here("src", "functions.R") %>% source()
here("src", "model_functions.R") %>% source()
here("src", "display_globals.R") %>% source()
```

# Farm location data {#sec-farm-location-data}

```{r load-farm-locations}
#| code-summary: Load farm location data and land polygons

library(sf)
library(rnaturalearth)

assigned_farms <- file.path(prepdata_path, "assigned_farms.qs") %>%
  qs_read() %>%
  filter(ISO3_Code == "NOR" & model_name == "rainbow_trout")

farm_IDs <- assigned_farms %>% pull(farm_ID)

land <- ne_countries(scale = "large", returnclass = "sf")
```

```{r fig-farm-location-map}
#| code-summary: Plot farm locations on a map of Norway
#| fig-cap: "Farm locations coloured by farm_ID (matching the production line plot)"

# Build a shared colour scale so both plots use identical farm_ID colours
farm_factor_levels <- assigned_farms %>% 
  mutate(latitude = st_coordinates(geometry)[2]) %>% 
  arrange(latitude) %>% 
  pull(farm_ID)
farm_colours <- viridis::viridis(length(farm_factor_levels), option = "turbo")
names(farm_colours) <- as.character(farm_factor_levels)

# Bounding box around Norway for cropping
norway_bbox <- st_bbox(c(xmin = 4, xmax = 31, ymin = 57, ymax = 72),
                       crs = st_crs(4326))

ggplot() +
  geom_sf(data = land %>% st_make_valid() %>% st_crop(norway_bbox), fill = "grey90", colour = "grey50") +
  geom_sf(
    data = assigned_farms %>% mutate(farm_ID = as.factor(farm_ID)),
    aes(colour = farm_ID),
    size = 3
  ) +
  scale_colour_manual(values = farm_colours) +
  theme_void() +
  labs(colour = "Farm ID")
```

# Production data {#sec-get-data}

```{r load-production-files}
#| code-summary: Load production file names and extract farm IDs

prod_fnms <- file.path(outs_path, "data", "farm_production") %>%
  list.files(full.names = T) %>%
  str_subset("MC100.qs")

all_farm_IDs <- prod_fnms %>%
  basename() %>%
  str_extract("(?<=farmID_)\\d+") %>%
  as.integer()

prod_fnms <- prod_fnms[which(all_farm_IDs %in% farm_IDs)]
```

# Exploring data {#sec-exploring-data}

```{r helper-function}
#| code-summary: Define helper function to tidy production statistics

tidy_stat <- function(prod_data, stat_name) {
  imap_dfr(prod_data, function(year_data, year_name) {
    tibble(
      year = as.integer(year_name),
      day  = year_data$days,
      mean = year_data$stats[[stat_name]][, 1],
      sd   = year_data$stats[[stat_name]][, 2]
    ) %>% 
      mutate(prod_day = day - min(day) + 1)
  })
}

qs_read(prod_fnms[1])[[1]] %>% str()
```

## Farm biomass {#sec-farm-biomass}

```{r process-farm-biomass}
#| code-summary: Process farm biomass statistics across all farms

biomass_stats <- map2_dfr(
  prod_fnms,
  farm_IDs,
  function(fnm, ID) {
    tidy_stat(qs_read(fnm), "weight_scaled") %>% 
      mutate(farm_ID = ID)
  },
  .progress = T
)
```

```{r fig-farm-biomass-over-time}
#| code-summary: Plot farm biomass over time by farm ID
#| fig-cap: "Farm biomass harvest in each year of production, coloured by farm ID."

biomass_stats %>%
  group_by(farm_ID, year) %>%
  slice_tail(n = 1) %>%
  ungroup() %>% 
  ggplot(aes(x = year, y = mean/1000000, colour = as.factor(farm_ID))) +
  geom_line(linewidth = 0.75) +
  scale_colour_manual(values = farm_colours) +
  prettyplot() +
  labs(colour = "Farm ID", x = "Year", y = "Farm biomass (t)")
```

## Feed ingested (provided) {#sec-feed-ingested}

```{r process-feed-ingested}
#| code-summary: Process feed ingested statistics across all farms

feed_stats <- map2_dfr(
  prod_fnms,
  farm_IDs,
  function(fnm, ID) {
    tidy_stat(qs_read(fnm), "ing_act_scaled") %>% 
      mutate(farm_ID = ID)
  },
  .progress = T
)
```

```{r fig-total-feed-provided}
#| code-summary: Plot total feed provided per farm over time
#| fig-cap: "Total feed provided to each farm over its whole production cycle in each harvest year. All farms are here assumed to provide ~7% more feed than actually required (feeding efficiency = 95%, overfeeding = 1.5%)"

feed_stats %>%
  group_by(farm_ID, year) %>%
  reframe(mean = sum(mean, na.rm = T)) %>%
  ungroup() %>% 
  ggplot(aes(x = year, y = 1.069519 * mean/1000000, colour = as.factor(farm_ID))) +
  geom_line(linewidth = 0.75) +
  scale_colour_manual(values = farm_colours) +
  prettyplot() +
  labs(colour = "Farm ID", x = "Year", y = "Feed provided (t)")
```

## Feed provided per biomass {#sec-feed-per-biomass}

```{r calculate-feed-per-biomass}
#| code-summary: Calculate feed provided per harvested biomass

feed_biomass_stats <- left_join(
  biomass_stats %>% 
    select(-sd) %>% 
    group_by(farm_ID, year) %>%
    slice_tail(n = 1) %>%
    ungroup(), 
  feed_stats %>%
    group_by(farm_ID, year) %>%
    reframe(mean = sum(mean, na.rm = T)) %>%
    ungroup(),
  by = join_by(farm_ID, year)
) %>% 
  mutate(mean = 1.069519 * mean.y/mean.x) %>% 
  select(-c(mean.y, mean.x))
```

```{r fig-feed-per-biomass}
#| code-summary: Plot feed provided per harvested biomass over time
#| fig-cap: "Total feed provided to each farm over its whole production cycle per harvested biomass. All farms are assumed to provide ~7% more feed than actually required (fish feeding efficiency = 95%, overfeeding = 1.5%)."

feed_biomass_stats %>%
  ggplot(aes(x = year, y = mean, colour = as.factor(farm_ID))) +
  geom_line(linewidth = 0.75) +
  scale_colour_manual(values = farm_colours) +
  prettyplot() +
  labs(colour = "Farm ID", x = "Year", y = "Feed provided/harvested biomass")
```

```{r feed-ingredients}

rms_df <- read_excel(here("data", "raw_data", "feed_profiles_and_composition.xlsx"), sheet = "all_feeds") %>%
  select(feed, ingredient, proportion) %>% 
  filter(feed == "Rainbow trout 1") %>% 
  mutate(raw_material = case_when(
    ingredient %in% c("canola-oil") ~ "canola",
    ingredient %in% c("coconut-oil") ~ "coconut",
    ingredient %in% c("faba-beans") ~ "faba",
    ingredient %in% c("fishmeal-forage", "fish-oil-forage") ~ "fish (forage)",
    ingredient %in% c("fishmeal-trimmings", "fish-oil-trimmings") ~ "fish (trimmings)",
    ingredient %in% c("guar-meal") ~ "guar",
    ingredient %in% c("linseed-oil") ~ "linseed",
    ingredient %in% c("pea-flour", "pea-protein-concentrate") ~ "pea",
    ingredient %in% c("soy-protein-concentrate", "soybean-oil") ~ "soy",
    ingredient %in% c("sunflower-meal") ~ "sunflower",
    ingredient %in% c("wheat", "wheat-gluten") ~ "wheat"
  )) %>% 
    group_by(raw_material) %>% 
    reframe(proportion = sum(proportion))
```

```{r}
#| fig-cap: "Total raw material requirement in each year of production."

feed_stats %>%
  group_by(year) %>%
  reframe(mean = sum(1.069519*mean, na.rm = T)) %>%
  ungroup() %>% 
  cross_join(rms_df) %>% 
  mutate(mean_rm = mean * proportion) %>% 
  ggplot(aes(x = year, y = mean_rm/1000000, colour = as.factor(raw_material))) +
  geom_line(linewidth = 0.75) +
  prettyplot() + theme(legend.position = "right") +
  labs(colour = "Farm ID", x = "Year", y = "Raw material required (t)")
```

# Deciding on MC simulation sizes

How many MC runs per farm is necessary?

```{r get-mc-files}

prod_fnms <- file.path(outs_path, "data", "farm_production") %>% 
  list.files(recursive = T, full.names = T)

all_farm_IDs <- prod_fnms %>%
  basename() %>%
  str_extract("(?<=farmID_)\\d+") %>%
  as.integer()

prod_fnms <- prod_fnms[which(all_farm_IDs %in% farm_IDs)]

prod_fnms <- list(
  prod_fnms %>% str_subset("MC10.qs"),
  prod_fnms %>% str_subset("MC100.qs"),
  prod_fnms %>% str_subset("MC1000.qs"),
  prod_fnms %>% str_subset("MC2500.qs"),
  prod_fnms %>% str_subset("MC5000.qs")
)
```

```{r load-mc-data}
prod_mc <- map_dfr(
  prod_fnms,
  function(fnms) {
    map_dfr(fnms, function (fnm) {
      rbind(
        tidy_stat(qs_read(fnm), "weight_scaled") %>% 
          group_by(year) %>% 
          slice_tail(n = 1) %>% 
          ungroup() %>% 
          select(-day, -prod_day) %>% 
          mutate(stat = as.factor("weight_scaled")),
        tidy_stat(qs_read(fnm), "ing_act_scaled") %>% 
          group_by(year) %>% 
          reframe(mean = sum(mean, na.rm = T),
                  sd = sqrt(sum(sd^2, na.rm = T))) %>% 
          mutate(stat = as.factor("ing_act_scaled"))
        ) %>% 
        mutate(
          farm_ID = fnm %>% basename() %>% str_extract("(?<=farmID_)\\d+") %>%  as.integer(),
          MC = fnm %>% basename() %>% str_extract("(?<=MC)\\d+") %>% as.factor()
        )
    })
  },
  .progress = T
)

# Take difference from the 5000 MC run
mc_levels <- unique(prod_mc$MC)
ref <- "5000"

prod_mc <- map_dfr(
  split(prod_mc, prod_mc$farm_ID), 
  function(df) {
    df %>%
      pivot_wider(
        names_from = MC,
        values_from = c(mean, sd)
      ) %>%
      mutate(
        across(
          all_of(paste0("sd_", mc_levels)),
          ~ sqrt((.x / get(paste0("mean_", cur_column() %>% str_extract("\\d+")))) ^2 +
                (get(paste0("sd_", ref)) / get(paste0("mean_", ref)))^2),
          .names = "{.col}"
        ),
        across(
          all_of(paste0("mean_", mc_levels)),
          ~ get(paste0("mean_", ref)) - .x
        )
      ) %>%
      mutate(
        across(
          all_of(paste0("sd_", mc_levels)),
          ~ .x * get(paste0("mean_", cur_column() %>% str_extract("\\d+")))
        ),
        !!paste0("mean_", ref) := 0,
        !!paste0("sd_", ref) := NA
      ) %>%
      pivot_longer(
        cols = matches("^(mean|sd)_"),
        names_to = c(".value", "MC"),
        names_sep = "_"
      )
  }
)
```

At first pass, the MC-10 run is obviously giving wildly different results than the others (@fig-MC-pass-1).

```{r fig-MC-pass-1}
#| fig-cap: Difference between the 5000-individual run (MC-5000) and a selection of runs with smaller MC sample sizes on harvested final biomass (left) and ingested feed (right). A selection of 6 farms is shown here.

prod_mc %>% 
  filter(farm_ID %in% sample(farm_IDs, 6)) %>% 
  ggplot(aes(x = year, y = mean, ymin = mean-sd, ymax = mean+sd, colour = MC, fill = MC)) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(alpha = 0.25) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  prettyplot() +
  theme(legend.position = "bottom") +
  facet_grid(rows = vars(farm_ID), cols = vars(stat))
```

```{r fig-MC-pass-2}
#| fig-cap: Difference between the 5000-individual run (MC-5000) and a selection of runs with smaller MC sample sizes on harvested final biomass (left) and ingested feed (right). A selection of 6 farms is shown here, and the MC-10 sample run has been removed.

prod_mc %>% 
  filter(farm_ID %in% sample(farm_IDs, 6) & MC != c("10")) %>% 
  ggplot(aes(x = year, y = (mean), ymin = (mean-sd), ymax = (mean+sd), colour = MC, fill = MC)) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(alpha = 0.25) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  prettyplot() +
  theme(legend.position = "bottom") +
  facet_grid(rows = vars(farm_ID), cols = vars(stat))
```

```{r average-diff}
prod_mc %>% 
  group_by(stat, MC) %>% 
  reframe(mean_diff = mean(abs(mean), na.rm = T) %>% set_units("g") %>% set_units("t")) %>% 
  gt()
```

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Run production](05_01_run_production_seabream.qmd)

[Next: Home →](../index.qmd)
:::
