---
title: "7: Habitat suitability"
subtitle: "FAO Climate Change Risks to Fed Mariculture"
author:
  - "Tormey Reimer"
date: last-modified
---

::: {style="display: flex; justify-content: space-between;"}
[← Previous: Explore production](06_explore_production.qmd)

[Next: Home →](../index.qmd)
:::

# Overview {#sec-overview}

```{r setup}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: "Load packages and set display globals"

library(tidyverse)
library(patchwork)
library(terra)
library(qs2)
library(terra)
library(tidyterra)
library(sf)
library(rnaturalearth)
library(lubridate)
library(cmocean)
library(here)
```

```{r source-scripts}
#| cache: false
#| echo: false
#| warning: false
#| message: false
#| output: false
#| code-summary: "Source R scripts in use"

here("src", "dirs.R") %>% source()
here("src", "other_functions.R") %>% source()
here("src", "model_functions.R") %>% source()
here("src", "country_bboxes.R") %>% source()
```

# Overview {#sec-overview}

"Habitat suitability" (HS) here refers to the daily feeding response of a species [0-1]. Originally, habitat suitability was going to me measured via two mechanisms: feeding response and metabolic response (catabolism at half-weight - anabolism). This was simplified to just feeding response for a few reasons:

1. By its nature, catabolism - anabolism includes feeding response in its calculation, meaning that feeding response is double-counted when both measures are used.
2. Since catabolism always increases with temperature (albeit by different slopes) all the interesting changes in HS come from changes in the feeding response.
3. When placed side by side, it is very difficult to tell (visually) if there are any significant differences in HS from the two measures.

This document calculates habitat suitability for all 16 model species within the EEZ areas of all countries currently producing marine fed mariculture.

# Species parameters {#sec-species-params}

```{r load-parameters}
#| code-summary: 'Load species parameters for all models'

params_files <- file.path(prepdata_path, "species_parameters") %>% 
  list.files(full.names = T)

model_names <- params_files %>% 
  basename() %>% 
  str_remove_all("species_parameters_|.qs")

parameters_species <- map(params_files, qd_read) %>% 
  setNames(model_names)

# Feed parameters
feed_params <- file.path(prepdata_path, "feed_parameters") %>% 
  list.files(full.names = T)

feed_names <- feed_params %>% 
  basename() %>% 
  str_remove_all(".qs")

feed_params <- map(feed_params, qs_read) %>% 
  setNames(feed_names)

model_names <- names(parameters_species) %>% str_subset("golden_pompano", negate = T)
```

# Habitat suitability per country/species

```{r temperatures-and-seacells}
#| code-summary: Get all the necessary data

EEZ_by_FAO_full <- file.path(prepdata_path, "EEZ_data_with_FAO_regions.qs") %>%
  qd_read() %>%
  st_transform(crs = 4326) %>%
  st_make_valid()

tos_rast_fnms <- file.path(bigdata_path, "ESGF", "EC-Earth3P-HR", "projected_adjusted") %>% 
  list.files(full.names = T) %>% 
  sort()
tos_dates <- str_extract(basename(tos_rast_fnms), "\\d{4}-\\d{2}-\\d{2}")
tos_rast_fnms_annual <- split(tos_rast_fnms, year(as.Date(tos_dates)))
```

HS is calculated per country (EEZ), per species (model_name), per harvest year, and per day. The annual habitat suitability is then calculated as the sum of all days. 

```{r}
country_dirs  <- unique(EEZ_by_FAO_full$ISO3_Code)
harvest_years <- 2015:2099
```

Habitat suitability is calculated for all species in all countries, even if that species is not currently farmed there. This is in case we want to go back to that - in the consolidation phase, only species actually grown in each country will count towards the overall habitat suitability score.

```{r save-habitat-suitability}
#| code-summary: "Main harvest year → species → country habitat suitability loop"
#| eval: false

# ── Create all filenames & directories ─────────────────────────────────────
files_HS <- tidyr::crossing(country_dirs, model_names, harvest_years) %>%
  glue::glue_data("{country_dirs}/{model_names}/FR_{harvest_years}.tif") %>%
  as.character() %>%
  here("outputs/data/habitat_suitability", .)

dirs <- unique(dirname(files_HS))
for (d in dirs) dir.create(d, recursive = TRUE, showWarnings = FALSE)

# ── Pre-project EEZ polygons to raster CRS ────────────────────────────────
ref_rast  <- rast(tos_rast_fnms[1])
ref_crs   <- crs(ref_rast)
EEZ_vects <- EEZ_by_FAO_full %>%
  split(.$ISO3_Code) %>%
  map(~ vect(.x) %>%
        aggregate(by = "ISO3_Code") %>% # combine all fishing regions into a single EEZ per country
        project(ref_crs))

# ── Create a binary EEZ-union mask raster ─────────────────────────────────
# Rasterise the union of all EEZs onto the SST grid so we can mask ocean cells outside any EEZ to NA before running the model.
sf_use_s2(FALSE)
eez_union <- EEZ_by_FAO_full %>%
  st_make_valid() %>%      # GEOS make_valid can handle the crossing rings
  st_union() %>%
  st_as_sf()
sf_use_s2(TRUE)            # restore the default for later operations

eez_union_v <- project(vect(eez_union), ref_crs)
eez_mask   <- rasterize(eez_union_v, ref_rast, field = 1)  # 1 inside EEZ, NA outside
rm(ref_rast, eez_union, eez_union_v); gc()

# ── MAIN LOOP ─────────────────────────────────────────────────────────────
# For each havest year...
walk(
  harvest_years,
  function(yr) {
    # 1. Work out which species still need output files for this year
    yr_files_FR <- map(
      set_names(model_names),
      ~ here("outputs/data/habitat_suitability", country_dirs, .x, paste0("FR_", yr, ".tif"))
    )
    species_todo <- names(yr_files_FR)[!map_lgl(yr_files_FR, ~ all(file.exists(.x)))]

    if (length(species_todo) != 0) {
      # 2. Read SST for this year (only now that we know it's needed)
      yr_char       <- as.character(yr)
      this_tos_fnms <- tos_rast_fnms[str_detect(tos_dates, yr_char)]
      tos_stack_global <- rast(this_tos_fnms)

      # Apply the EEZ-union mask so that open ocean == NA
      tos_stack_global <- tos_stack_global * eez_mask

      for (sp in species_todo) {
        yr_sp_files_FR <- yr_files_FR[[sp]]

        # 3. Run model ONCE on the (masked) global stack
        resp_global <- get_feeding_responses_r(
          temp_stack     = tos_stack_global,
          species_params = parameters_species[[sp]]
        )

        # 4. Sum across days to get a single-layer global raster
        FR_global <- app(resp_global[["feeding_response"]], sum, na.rm = TRUE)
        rm(resp_global); gc()

        # 5. Crop/mask single-layer results per country
        for (i in seq_along(country_dirs)) {
          fnm_FR <- yr_sp_files_FR[i]
          if (file.exists(fnm_FR)) next

          eez_v      <- EEZ_vects[[country_dirs[i]]]
          fr_country <- crop(FR_global, eez_v) %>% mask(eez_v)

          writeRaster(fr_country, fnm_FR, overwrite = TRUE)
        }

        rm(FR_global); gc()
      }
    }
  },
  .progress = T
)
```

Habitat suitability is then saved per country EEZ, per species, and per decade (manually defined). Since it would be way too many plots to show HS (or relative change in HS) over all production years, instead we're going to save absolute HS in each decade and relative change in HS compared to the reference.

We also decided to save HS in "global warming levels" using the corresponding periods defined in [Table 1 here](https://climatedata.ca/resource/introduction-to-global-warming-levels/).

```{r decadal-HS}
#| code-summary: Calculate (absolute) decadal mean HS rasters per country and species

# Decade periods for each temperature are detailed in Table 1 here: 

decades <- list(
  "ref_2015_2024" = 2015:2024,
  "dec_2020_2029" = 2020:2029,
  "dec_2030_2039" = 2030:2039,
  "dec_2040_2049" = 2040:2049,
  "dec_2050_2059" = 2050:2059,
  "dec_2060_2069" = 2060:2069,
  "dec_2070_2079" = 2070:2079,
  "dec_2080_2089" = 2080:2089,
  "dec_2090_2099" = 2090:2099,
  "GLW_1.5" = 2018:2037,
  "GLW_2.0" = 2032:2051,
  "GLW_3.0" = 2055:2074,
  "GLW_4.0" = 2075:2094
)
HS_dir     <- file.path(outs_path, "data", "habitat_suitability")
HS_dec_dir <- file.path(outs_path, "data", "habitat_suitability_decadal")

# Per country, list annual FR files split by model name
country_ls <- map(
  set_names(country_dirs),    # cd <- country_dirs[1]
  function(cd) {
    FR_files <- list.files(file.path(HS_dir, cd), full.names = T, recursive = T, pattern = "FR_") %>% sort()
    split(FR_files, basename(dirname(FR_files)))
  }
)

# For each model_name and country, take the average HS over the specified decadal range
iwalk(
  country_ls,           # cls <- country_ls[[1]]; iso <- names(country_ls)[1]
  function(cls, iso) {
    # Output dirs mirror the input structure: <HS_dec_dir>/<iso>/<model_name>
    dec_dirs <- file.path(HS_dec_dir, iso, names(cls))
    walk(dec_dirs, dir.create, recursive = TRUE, showWarnings = FALSE)

    walk2(
      cls,              # mls <- cls[[1]]
      dec_dirs,         # mdir <- dec_dirs[[1]]
      function(mls, mdir) {
        # Group files by decade
        mls_yrs <- as.integer(str_extract(basename(mls), "\\d{4}(?=\\.tif$)"))
        mls_by_decade <- lapply(decades, \(d) mls[mls_yrs %in% d])
        mls_by_decade <- Filter(length, mls_by_decade) # filter out empty decades for now

        iwalk(
          mls_by_decade,          # dec_files <- mls_by_decade[[1]]; dec_name <- names(mls_by_decade)[1]
          function(dec_files, dec_name) {
            rast(dec_files) %>%
              app("mean", na.rm = T) %>%
              writeRaster(filename = file.path(mdir, paste0(dec_name, ".tif")), overwrite = T)
          }
        )
      }
    )
  },
  .progress = T
)
```

```{r relative-decadal-change}
#| code-summary: For each country EEZ and model species get the relative change in habitat suitability score for each decade, relative to a reference period.

rel_HS_dir <- file.path(outs_path, "data", "habitat_suitability_decadal_change")
country_relHS_dirs <- file.path(rel_HS_dir, country_dirs)
for (d in country_relHS_dirs) dir.create(d, recursive = TRUE, showWarnings = FALSE)

ref_period <- "ref_2015_2024"

walk(
  country_dirs,       # cd <- country_dirs[1]
  function(cd) {
    model_dirs <- file.path(rel_HS_dir, cd, model_names)
    for (d in model_dirs) dir.create(d, recursive = TRUE, showWarnings = FALSE)
    
    country_dec_files <- file.path(outs_path, "data", "habitat_suitability_decadal", cd) %>% 
      list.files(full.names = T, recursive = T)
    
    for (mn in model_names) { # mn <- model_names[1]
      model_dec_files <- country_dec_files %>% str_subset(pattern = mn)
      ref_file <- model_dec_files %>% str_subset(pattern = ref_period)
      model_dec_files <- setdiff(model_dec_files, ref_file)

      ref_rast <- rast(ref_file)
      dec_rasts <- rast(model_dec_files)
      names(dec_rasts) <- str_remove_all(basename(model_dec_files), ".tif")

      dec_rasts_change <- (dec_rasts - ref_rast) / ref_rast
      writeRaster(
        dec_rasts_change,
        file.path(rel_HS_dir, cd, mn, paste0(names(dec_rasts_change), "__", ref_period, ".tif")),
        overwrite = T
      )
    }
  },
  .progress = T
)
```

# Re-consolidate habitat suitability

Finally, we narrow down the HS files to those that we actually want to plot. For now, we're going to look at:

- The species that are actually grown in each country
- The decades 2030:2039, 2060:2069, and 2090:2099

```{r save-HS-country-plots}
#| code-summary: Save plots of habitat suitability

# This fills out 1 cell of border around the EEZ HS values, purely to stop the ugly white spaces between the coast and the HS data.
# Note that this gapfilling technically extrapolates "fake" data outside the country's EEZ
gapfill <- T

# Load all the bbox data (re-do if you made any changes to the CSV)
country_bbox_data <- load_country_bbox_data()

# Get assigned farms again, convert to nice crs
assigned_farms <- file.path(prepdata_path, "assigned_farms.qs") %>% qs_read() %>% st_transform(4326)
countries <- sort(unique(assigned_farms$ISO3_Code))

# Create directories
dirs <- file.path(outs_path, "plots", "habitat_suitability_decadal", countries)
for (d in dirs) dir.create(d, recursive = TRUE, showWarnings = FALSE)

# Get land polygon for plotting
land <- ne_countries(scale = "large", returnclass = "sf")

# Generate and save all files for each country
# iso <- countries[12]
walk(
  countries,
  function(iso) {
    country_data <- country_bbox_data[[iso]]
    country_bbox <- bbox(iso, crs = 4326)

    country_farms <- assigned_farms %>% 
      filter(ISO3_Code == iso)

    # Get all the data files but restrict to species actually being farmed there
    models_inuse <- country_farms %>% pull(model_name) %>% unique()
    HS_files <- file.path(outs_path, "data",  "habitat_suitability_decadal", iso) %>% 
      list.files(recursive = T, full.names = T) %>% 
      str_subset(paste0(models_inuse, collapse = "|"))

    # Plotset 1: Save plots for each model seperately
    # mn <- models_inuse[2]
    for (mn in models_inuse) {
      title_text <- paste0(country_data$name, " (", mn, ") habitat suitability")
      dir.create(file.path(HS_plot_path, iso, mn), recursive = TRUE, showWarnings = FALSE)

      dec_files <- HS_files %>% str_subset(mn)
      if (length(dec_files) == 0) {next}

      # Load data and rescale to [0,1] from [0,365]
      dec_data <- rast(dec_files)
      dec_data <- dec_data/365
      if (gapfill) {
        dec_data <- lapply(dec_data, \(x) focal(x, 3, "mean", na.rm = TRUE, na.policy = "only"))
        dec_data <- rast(dec_data)
      }
      names(dec_data) <- basename(dec_files)

      model_farms <- country_farms %>% 
        filter(model_name == mn)

      walk2(
        1:nlyr(dec_data),
        str_remove_all(names(dec_data), ".tif"),
        function(dd, nm) {
          subtitle_text <- if (str_detect(nm, "dec_")) {
            paste("Decade:", str_replace(str_remove(nm, "dec_"), "_", "-"))
          } else if (str_detect(nm, "ref_")) {
            paste("Reference period:", str_replace(str_remove(nm, "ref_"), "_", "-"))
          } else {
            str_replace(nm, "_", ": ")
          }
          file_text  <- paste0(iso, "_", mn, "_HS_", str_replace(names(dec_data[[dd]]), ".tif", ".png"))

          p <- ggplot() +
            geom_spatraster(data = dec_data[[dd]]) +
            geom_sf(data = land, fill = "grey85", colour = "grey55", linewidth = 0.2) + 
            geom_sf(data = model_farms, shape = 4, size = 1.5, colour = "black") +
            coord_sf(
              xlim = c(country_bbox[["xmin"]], country_bbox[["xmax"]]), 
              ylim = c(country_bbox[["ymin"]], country_bbox[["ymax"]])
            ) +
            scale_fill_gradientn(
              limits = c(0, 1),
              colours = cmocean("thermal")(256), 
              na.value = "transparent"
            ) +
            labs(
              title = title_text, 
              subtitle = subtitle_text,
              fill = "HS", x = "Longitude", y = "Latitude"
            ) +
            guides(fill = guide_colourbar(
              theme = theme(
                legend.key.height     = unit(14, "lines"),
                legend.key.width      = unit(1, "lines"),
                legend.ticks          = element_line(colour = "white", linewidth = 0.4),
                legend.ticks.length   = unit(0.2, "lines"),
                legend.frame          = element_rect(colour = "grey30", linewidth = 0.3),
                legend.title.position = "top"
              )
            )) +
            theme_classic() +
            theme(
              legend.position = "right",
              legend.title    = element_text(hjust = 0.5)
            )

            save_map(p = p, filename = file.path(HS_plot_path, iso, mn, file_text), panel_width = 5, dpi = 300)
        }
      )
    }

    # # Plotset 2: Species are plotted together, weighted by current production
    # HS_list <- split(HS_files, basename(HS_files))

    # iwalk(
    #   HS_list,
    #   function(dec_files, idx) {
    #     print(paste(idx, length(dec_files)))
    #   }
    # )


  },
  .progress = T
)
```


::: {style="display: flex; justify-content: space-between;"}
[← Previous: Choosing species](01_choosing_species.qmd)

[Next: Assigning Locations →](04_assigning_locations.qmd)
:::
